### 2020-11-22 paper.tex
Initial Overleaf Import

% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.20 of 2017/10/04
%
\documentclass[runningheads]{llncs}
%
\usepackage{graphicx}
% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following line
% to display URLs in blue roman font according to Springer's eBook style:
% \renewcommand\UrlFont{\color{blue}\rmfamily}

\begin{document}
%
\title{Successively Linearized Reachability onboard  the F1/10 Platform\thanks{Supported by organization x.}}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Nathan Jewell\inst{1}\orcidID{0000-1111-2222-3333} \and
Houssam Abbas\inst{1}\orcidID{1111-2222-3333-4444} \and
Stanley Baak?\inst{3}\orcidID{2222--3333-4444-5555}}
%
\authorrunning{N. Jewell et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Oregon State University, Corvallis OR 97333, USA \and
\email{jewelln@oregonstate.edu}}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
Reachability computations allow for validating safety parameters in various control systems. In this paper we analyze the performance characteristics of successively linearized reachability problems running in realtime. Importantly, we test these running alongside a full suite of autonomous control and localization tools onboard the F1/10 racing platform. A number of runtime modes which utilize single core and multiple core CPU as well as hybridized CPU/GPU were analyzed. In our testing we achieve accurate 10-step reachability as quickly as xxxxx seconds. We find that porting portions of reachability onto the GPU can improve the runtime by xxxx\% and reduces the computational complexity in relation to number of reachability steps.

\keywords{Reachability  \and Safety Analysis \and CUDA }
\end{abstract}
%
%
%
\section{Introduction}
Reachability is the computation and interpretation of possible future agent states at a time or set of times. Given an agent's current state and a range of possible future inputs, a reachability algorithm outputs information about all possible states of the agent at time T in the future. For computational efficiency and practical use, we discuss discrete-time reachability algorithms. In discrete-time reachability, a range of N possible state spaces are generated for N future times. defined by intervals spaced by the discretization time step, dt. Importantly the generated state spaces are minimal overapproximations of possible states as defined by the agent’s dynamical model. This guarantees that any state actually reached at time T is within the overapproximation boundary and can be utilized for safety analysis.

Safety verification is the overarching goal for reachability computations. With highly reliable systems, it is necessary to verify that no error state could be reached. In autonomous vehicles, error states may involve intersections with walls, other cars or people, etc.. By checking the overapproximation of states, it can be determined if the agent is in danger of reaching an error mode in the future. Planned inputs can then be modified to avoid the danger, preventing potentially catastrophic system failure.

We explore a number of different runtime modes for profiling successively linearized reachability computation. These modes are chosen to stress different components of the host system, improve runtime, and demonstrate the effectiveness of real time safety analysis alongside real-world loads.

\section{Setup}

\subsection{Runtime Modes}

\subsubsection{HYLAA} \newline The original hybrid reachability tool [cite].
\subsubsection{Quickzono Single Core} [QZ\_CPU] \newline A simplified subset of HYLAA code with succinct wrappers.  \\
\subsubsection{Quickzono Multiple Core} [QZ\_MP] \newline Quickzono code with a trivial CPU-based multiprocessing model \newline applied to the projection step. \\
\subsubsection{Quickzono GPU Dummy} [QZ\_DUMMY] \newline Quickzono with data copied to and from the GPU but running\newline a dummy kernel on the GPU which does no computation of the projection. \\
\subsubsection{Quickzono GPU Hybrid} [QZ\_HYBRID] \newline Hybrid GPU/CPU implementation, with the most taxing\newline part of the projection algorithm moved onto the GPU device. \\

\subsection{Offline Execution}
\subsection{Offline Execution}
\subsection{Performance Characteristics}
There are a number of important characteristics needed to describe the performance of a real time embedded algorithm.

Correctness is the assuredness that the outputs are a valid solution to the problem. It is important to know that the algorithm is producing results consistent with the desired output and underlying mathematics. This is especially important for a reachability algorithm which is utilized in safety analysis protocols.

Scalability is how well the algorithm scales with increased problem size. In our case, problem size is dictated by the number of time steps. This corresponds to either or both of an increase in horizon or decrease discretization time step. Horizon (sec) = \#time-step * time-step. It is important to understand how the algorithm scales so intelligent decisions can be made about optimal horizon and precision in real time applications.

Runtime is the time to solve the given problem. Minimizing runtime is a critical component of this research. Running a real time safety algorithm is only effective when there is a low latency between consecutive executions. If this criteria is not met, safety analysis could be out of date when the agent is developing a response, resulting in ineffective performance. In contrast, low latency [runtime] will improve the safety margin of the agent by providing reachability information to the controller which is very up to date with the environment.

Runtime variability is the standard deviation in the runtime. While latency is of primary importance, the consistency of the algorithm runtime is paramount for critical systems. Latency spikes at the wrong time could create dangerous problems for the agent when reacting to unsafe conditions.

\section{Methods}
\subsection{Collected Data}
Each characteristic has an empirical measure which we can use to analyze it quantitatively. Our offline and online profiling are run separately to evaluate the impact of running the reachability along with localization and control algorithms.

To validate correctness, we used HYLAA model output, assuming that HYLAA is mathematically consistent. Outputs from other runtime modes are compared to the HYLAA output to determine if there are any significant differences. It is not necessary to validate correctness separately for online and offline computation since the same code is executed in each case.

To validate scalability, each runtime model is tested with a range of values for the number of reachability steps which are representative of useful workloads. The number of steps (N) is equal to the ratio between total horizon time in seconds (T) and the discretization time-step (dt). This varying of step values is done for both online and offline modes. However, for online trials, only models capable of running around 200ms per iteration (5hz) are considered.

To test runtime, each combination of runtime mode and steps is evaluated over multiple trials. The recorded runtimes will be the average over 200 trials. This data collection is done for both online and offline testing.

To test runtime variability, the all recorded runtimes from all trials are analyzed. We compute standard deviation in runtime and 95% runtime confidence intervals around the mean assuming normally distributed variation in runtimes. This analysis is performed for both online and offline testing.

Some other values are also collected for the benefit of running analysis. 
What is a trial? One execution of the reachability computation.

\section{Results}

\section{Discussion}

\begin{figure}
\includegraphics[width=\textwidth]{fig1.eps}
\caption{A figure caption is always placed below the illustration.
Please note that short captions are centered, while long ones are
justified by the macro package automatically.} \label{fig1}
\end{figure}

%
% ---- Bibliography ----
%
% BibTeX users should specify bibliography style 'splncs04'.
% References will then be sorted and formatted in the correct style.
%
% \bibliographystyle{splncs04}
% \bibliography{mybibliography}
%
\begin{thebibliography}{8}

\bibitem{ref_hylaa}
HYLAA Author, F., Author, S.: Title of a proceedings paper. In: Editor,
F., Editor, S. (eds.) CONFERENCE 2016, LNCS, vol. 9999, pp. 1--13.
Springer, Heidelberg (2016). \doi{10.10007/1234567890}

\bibitem{ref_oder}
ODER Author, F., Author, S., Author, T.: Book title. 2nd edn. Publisher,
Location (1999)

\end{thebibliography}
\end{document}

### 2020-11-23 copy_media.sh
graph copy script and initial graphs

@@ -1,0 +1,1 @@
+cp -r /home/nathan/Desktop/tx2-hosted/cuda-src/ppcm/reachability/scripts/profiler ./profiler_out

### 2020-11-23 paper.tex
Updates from Overleaf

@@
 \usepackage{graphicx}
+\usepackage{subcaption}
+\usepackage{float}
 % Used for displaying a sample figure. If possible, figure files should
@@
 %
-\title{Successively Linearized Reachability onboard  the F1/10 Platform\thanks{Supported by organization x.}}
+\title{Successively Linearized Onboard Reachability\thanks{Supported by organization x.}}
 %
@@
 \subsubsection{HYLAA} \newline The original hybrid reachability tool [cite].
-\subsubsection{Quickzono Single Core} [QZ\_CPU] \newline A simplified subset of HYLAA code with succinct wrappers.  \\
-\subsubsection{Quickzono Multiple Core} [QZ\_MP] \newline Quickzono code with a trivial CPU-based multiprocessing model \newline applied to the projection step. \\
-\subsubsection{Quickzono GPU Dummy} [QZ\_DUMMY] \newline Quickzono with data copied to and from the GPU but running\newline a dummy kernel on the GPU which does no computation of the projection. \\
-\subsubsection{Quickzono GPU Hybrid} [QZ\_HYBRID] \newline Hybrid GPU/CPU implementation, with the most taxing\newline part of the projection algorithm moved onto the GPU device. \\
+\vspace*{-5pt}
+\subsubsection{Quickzono Single Core} [QZ\_CPU] \newline A simplified subset of HYLAA code with succinct wrappers. 
+\vspace*{-5pt}
+\subsubsection{Quickzono Multiple Core} [QZ\_MP] \newline Quickzono code with a trivial CPU-based multiprocessing model \newline applied to the projection step. 
+\vspace*{-5pt}
+\subsubsection{Quickzono GPU Dummy} [QZ\_DUMMY] \newline Quickzono with data copied to and from the GPU but running\newline a dummy kernel on the GPU which does no computation of the projection. 
+\vspace*{-5pt}
+\subsubsection{Quickzono GPU Hybrid} [QZ\_HYBRID] \newline Hybrid GPU/CPU implementation, with the most taxing\newline part of the projection algorithm moved onto the GPU device. 
+\vspace*{-5pt}
 
-\subsection{Offline Execution}
-\subsection{Offline Execution}
+\subsection{Offline Profiling}
+In offline profiling, reachability is computed as the sole program running on the system.
+A dedicated testing script executes each of the runtime modes for 200 trials at intervals between 5 to 40 reachability steps.
+HYLAA is only tested up to 20 steps due to slow performance.
+The script outputs timing data excluding any one-off setup and configuration code.
+\subsection{Online Profiling}
+In online profiling, reachability is computed as part of a ROS network running physical control nodes (controller input, motor and servo control, etc..), a GPU based particle filter node for localization, a model predictive control node, and various other supporting nodes.
+Before beginning the profiling, the vehicle is placed into the test track, localized and configured to autonomously drive the track until profiling is complete.
+The reachability node is implemented as a wrapper for separate reachability classes (those called by the offline profiler) and records call timings for the same function, executing as quickly as possible.
+The online profiler is configured to automatically switch between runtimes modes and number of reachability steps.
+This occurs for the same parameters as in offline profiling except only those configurations executing at least 4hz (<=250ms per trial) are considered.
+HYLAA is not tested in this profiling due to slow performance.
 \subsection{Performance Characteristics}
@@
 
+\begin{figure}[H]
+\includegraphics[width=\textwidth]{profiler_out/all_avg_unified.png}
+\caption{Average trial execution times for all runtime modes in online and offline configuration.} \label{fig1}
+\end{figure}
+\begin{figure}[H]
+\includegraphics[width=\textwidth]{profiler_out/all_avg_unified.png}
+\caption{Average trial execution times for all runtime modes in online and offline configuration.} \label{fig1}
+\end{figure}
+\begin{figure}[H]
+    \subcaptionbox{Detail of the Quickzono GPU Hybrid runtimes with 95\% confidence intervals.\label{CPU_CI}}{\includegraphics[width=.5\linewidth]{profiler_out/avg_QZ-CPU_CI.png} }
+    \subcaptionbox{Detail of the Quickzono Single Core runtimes with 95\% confidence intervals.\label{MP_CI}}{\includegraphics[width=.5\linewidth]{profiler_out/avg_QZ-MP_CI.png} }
+\begin{subfigure}{\linewidth}
+    \includegraphics[width=.5\linewidth]{profiler_out/avg_QZ-HYBRID_CI.png}
+    \includegraphics[width=.5\linewidth]{profiler_out/avg_QZ-CPU_CI.png} \hfill
+
+\end{subfigure}
+
+\end{figure}
+
 \section{Discussion}
-
-\begin{figure}
-\includegraphics[width=\textwidth]{fig1.eps}
-\caption{A figure caption is always placed below the illustration.
-Please note that short captions are centered, while long ones are
-justified by the macro package automatically.} \label{fig1}
-\end{figure}
 

### 2020-11-25 copy_media.sh
new graphs

@@ -1,1 +1,1 @@
-cp -r /home/nathan/Desktop/tx2-hosted/cuda-src/ppcm/reachability/scripts/profiler ./profiler_out
+cp -r /home/dev/cuda-venv/src/ppcm/reachability/scripts ./profiler_out

### 2020-11-25 profiler_out/scripts/F1Hylaa.py

@@ -1,0 +1,225 @@
+# library imports
+from functools import partial
+from scipy.io import loadmat
+import importlib
+
+#hylaa imports
+from hylaa.hybrid_automaton import HybridAutomaton 
+from hylaa.settings import HylaaSettings, PlotSettings, LabelSettings 
+from hylaa.core import Core
+from hylaa.stateset import StateSet
+from hylaa import lputil
+from matplotlib.patches import Circle, Ellipse
+from matplotlib import collections
+from matplotlib import pyplot as plt
+
+#local imports
+from nl_dynamics import F1Dynamics
+import simulator
+
+##ROS imports
+#import rospy
+#from osuf1_common import StampedFloat2d, MPC_metadata
+#from profilehooks import profile
+import cProfile as profile
+
+#wrapper to run hylaa repeatedly with different inputs
+class F1Hylaa:
+    def __init__(self):
+
+        # ------------------ Semi-Static Configuration ----------------------
+        self.settings = None #hylaa settings object
+        self.dt = None          #dt from MPC metdata
+        self.ttime = None
+
+        self.input_uncertainty = []
+        self.state_uncertainty = []
+
+        self.model = None       #dynamics abstraction object
+
+        #TODO automatic or otherwise validated variability
+        # ------------------ Per-run Configuration ----------------------
+        self.ha = None
+        self.predictions = None #predictions from MPC 3d array : [ dt[ state[x,y,psi], inputs[d,v] ] ]
+        self.modeList = []
+        self.initialState = None
+
+
+    def set_model_params(self, state_uncertainty, input_uncertainty, dynamics_module="kinematics_model"):
+        model_gen = importlib.import_module(dynamics_module)
+        self.modeList = []
+        self.state_uncertainty = state_uncertainty
+        self.input_uncertainty = input_uncertainty
+        self.model = model_gen.getModel()
+        self.model.setInputUncertainty(input_uncertainty)
+
+        return 1
+    
+    def run_hylaa(self, predictions):
+        self.ha = None
+        self.predictions = None
+        self.modeList = []
+        self.initialState = None
+
+        self.ha = HybridAutomaton()
+        self.predictions = predictions
+        self.graphPredictions()
+        self.make_automaton()
+
+        initialBox = self.make_init(self.predictions[0][0])
+        core = Core(self.ha, self.settings)
[…]

### 2020-11-25 profiler_out/scripts/F1QuickZono.py

@@ -1,0 +1,138 @@
+# library imports
+from functools import partial
+import importlib
+#from concurrent.futures import ThreadPoolExecutor, ProcessPoolExecutor
+#import dill
+from multiprocessing import Pool
+
+#local imports
+from nl_dynamics import F1Dynamics
+
+from quickzonoreach.zono import get_zonotope_reachset
+from quickzonoreach.zono_projection import ZP_TYPE, get_ZP_instance
+
+#wrapper to run quickzono repeatedly with different inputs
+class F1QuickZono:
+    def __init__(self):
+
+        # ------------------ Semi-Static Configuration ----------------------
+        self.dt = None          #dt from MPC metdata
+        self.ttime = None
+        self.num_steps = None
+
+        self.input_uncertainty = []
+        self.state_uncertainty = []
+
+        self.model = None       #dynamics abstraction object
+
+        #TODO automatic or otherwise validated variability
+        # ------------------ Per-run Configuration ----------------------
+        self.predictions = None #predictions from MPC 3d array : [ dt[ state[x,y,psi], inputs[d,v] ] ]
+
+        self.init_box = []
+        self.a_mat_list = []
+        self.b_mat_list = []
+        self.input_box_list = []
+        self.dt_list = []
+        self.save_list = []
+
+
+        self.ZP = None 
+
+
+    def set_model_params(self, state_uncertainty, input_uncertainty, dynamics_module="kinematics_model", runtime_mode="CPU"):
+        model_gen = importlib.import_module(dynamics_module)
+        self.modeList = []
+        self.state_uncertainty = state_uncertainty
+        self.input_uncertainty = input_uncertainty
+        self.model = model_gen.getModel()
+        self.model.setInputUncertainty(input_uncertainty)
+        
+        
+        self.ZP = get_ZP_instance(ZP_TYPE[runtime_mode])
+        return 1
+    
+    def run(self, predictions, profile=False):
+        self.predictions = predictions[:self.num_steps]
+
+        self.quick = True
+        self.a_mat_list = []
+        self.b_mat_list = []
+        self.input_box_list = []
+
+
+        #profile.runctx('resultprof = self.run_zono(initialBox, core)', globals(), locals(), filename="profiler/prof/out_tmp.prof")
+        #result = locals()['resultprof']
+        self.make_dynamics()
+        self.make_init(self.predictions[0][0])
+        zonos = self.run_zono()
+
+
+        #do projection for safety analysis in 2d
+        if profile:
[…]

### 2020-11-25 profiler_out/scripts/graph_maker.py

@@ -1,0 +1,281 @@
+import pandas as pd
+import scipy.stats
+import matplotlib.pyplot as plt
+import numpy as np
+
+import scipy.stats as st
+def get_best_distribution(data):
+    dist_names = ["norm", "exponweib", "weibull_max", "weibull_min", "pareto", "genextreme"]
+    dist_results = []
+    params = {}
+    for dist_name in dist_names:
+        dist = getattr(st, dist_name)
+        param = dist.fit(data)
+
+        params[dist_name] = param
+        # Applying the Kolmogorov-Smirnov test
+        D, p = st.kstest(data, dist_name, args=param)
+        dist_results.append((dist_name, p))
+
+    # select the best fitted distribution
+    best_dist, best_p = (max(dist_results, key=lambda item: item[1]))
+    # store the name of the best fit and its p value
+
+    print("Best fitting distribution: "+str(best_dist))
+    print("Best p value: "+ str(best_p))
+    #print("Parameters for the best fit: "+ str(params[best_dist]))
+
+    return best_dist, best_p, params[best_dist]
+
+upstatus = "Offline"
+csv_input = "raw/offline_FINAL.csv"
+csv_input_2 = "raw/online_FINAL.csv"
+
+
+import pdb
+columns = ["time", "steps", "mode", "verts"]
+timing_data = pd.read_csv(csv_input, sep=",", names=columns) 
+timing_data["env"] = pd.Series(["offline"] * len(timing_data), index=timing_data.index)
+timing_data_2 = pd.read_csv(csv_input_2, sep=",", names=columns)
+timing_data_2["env"] = pd.Series(["online"] * len(timing_data_2), index=timing_data_2.index)
+timing_data = pd.concat([timing_data, timing_data_2])
+
+
+
+print(timing_data[:6])
+
+modes = list(timing_data['mode'].unique())
+modes.remove("HYLAA")
+online_steps = timing_data.loc[timing_data['env']=="online"]['steps'].unique()
+offline_steps = timing_data.loc[timing_data['env']=="offline"]['steps'].unique()
+steps = offline_steps
+online_steps = [s for s in online_steps if s in offline_steps]
+envs = timing_data['env'].unique()
+conf_interval_prop = .95
+
+timing_stats = pd.DataFrame(
[…]

### 2020-11-25 profiler_out/scripts/hylaa_node.py

@@ -1,0 +1,136 @@
+#!/usr/bin/python3.6
+# library imports
+from functools import partial
+
+#local imports
+from F1Hylaa import F1Hylaa
+
+#ROS imports
+import rospy
+from std_msgs.msg import Header
+from osuf1_common.msg import MPC_trajectory, MPC_metadata, MPC_prediction, ReachSets, NPointSet, NPoint
+
+class HYLAA_node:
+    def __init__(self):
+
+        rospy.init_node("hylaa_node")
+
+        #self.modeList = None    #store list of all modes so we can retrieve correct reachsets
+        #self.initialBox = None  #we need to store the initial stateset
+        #self.core = None        #core object for running hylaa with settings
+
+        #---------------------------------------------------------
+        #                   HYLAA Params
+        #---------------------------------------------------------
+        self.predictions = None #predictions from MPC
+        self.reachability_horizon = rospy.get_param("/hylaa_node/horizon", 0)
+        self.dt = None          #dt from MPC metdata
+        self.mpc_horizon = None #simulation horizon from MPC metadata
+
+        #TODO automatic or otherwise validated variability
+        self.state_uncertainty = [
+            rospy.get_param("/hylaa_node/state_uncertainty/px", 0),
+            rospy.get_param("/hylaa_node/state_uncertainty/py", 0),
+            rospy.get_param("/hylaa_node/state_uncertainty/psi", 0),
+        ]
+
+        self.input_uncertainty = [
+            rospy.get_param("/hylaa_node/input_uncertainty/velocity", 0),
+            rospy.get_param("/hylaa_node/input_uncertainty/delta", 0)
+        ]
+
+
+        #custom horizon or utilize all computed MPC steps
+        self.hylaa_verbosity = rospy.get_param("/hylaa_node/output_verbosity", "VERBOSE").upper() #TODO integrate with roslogger 
+        self.graph_predictions = rospy.get_param("/hylaa_node/graph_predictions", False) #wether predicted sim results should be overlayed on reach set graph (if displayed)
+        self.displayType = rospy.get_param("/hylaa_node/display_type", "NONE").upper()
+        self.output = rospy.get_param("/hylaa_node/display_filename", "hylaa_reach.png") #TODO put images in distinct folder and label with frame times
+
+
+        #---------------------------------------------------------
+        #                   HYLAA Calling Vars
+        #---------------------------------------------------------
+        self.hylaa = F1Hylaa()
[…]

### 2020-11-25 profiler_out/scripts/hylaa_viz_node (copy).py

@@ -1,0 +1,97 @@
+#!/usr/bin/python
+#node to display reachsets as filled planes in rviz
+# subscribes to hylaa output topic
+# publishes RVIZ triangle list
+# configurable in hylaa_viz.yaml
+
+import rospy
+from osuf1_common.msg import ReachSets
+import tripy
+from visualization_msgs.msg import Marker, MarkerArray
+from geometry_msgs.msg import Pose, Point, Quaternion, Vector3
+from std_msgs.msg import Header, ColorRGBA
+from osuf1_common.msg import ReachSets
+from itertools import repeat
+
+#node to publish reachability visualization messages for viewing in rviz
+
+class Hylaa_Viz_Node:
+    def __init__(self):
+        rospy.init_node("hylaa_viz")
+
+
+        reach_sub_topic = rospy.get_param("/zono_node/reach_pub_topic", "reach_pub")
+        self.reachPub = rospy.Subscriber(reach_sub_topic, ReachSets, self.makeViz) 
+        sets_outline_topic = rospy.get_param("/hylaa_viz/outline_topic", "hylaa_viz_outline")
+        sets_tris_topic = rospy.get_param("/hylaa_viz/tris_topic", "hylaa_viz_tris")
+
+        self.outlinePub = rospy.Publisher(sets_outline_topic, MarkerArray, queue_size=1)
+        self.trisPub = rospy.Publisher(sets_tris_topic, Marker, queue_size=1)
+
+        self.tri_marker_id = 44
+        self.outline_marker_id = 555 # + n
+
+        self.colors = [(230, 25, 75), (60, 180, 75), (255, 225, 25), (0, 130, 200), (245, 130, 48), (145, 30, 180), (70, 240, 240), (240, 50, 230), (210, 245, 60), (250, 190, 190), (0, 128, 128), (230, 190, 255), (170, 110, 40), (255, 250, 200), (128, 0, 0), (170, 255, 195), (128, 128, 0), (255, 215, 180), (0, 0, 128), (128, 128, 128)]
+        self.colors = [ColorRGBA(c[0], c[1], c[2], 1) for c in self.colors]
+
+    def start(self):
+        rospy.spin()
+    
+    def makeViz(self, reachSets):
+        pointSets = [[tuple(p.p) for p in rs.set] for rs in reachSets.sets]
+        triangleSets = [tripy.earclip(ps) for ps in pointSets]
+
+
+        header = Header()
+        header.stamp = rospy.Time.now()
+        header.frame_id = reachSets.header.frame_id
+
[…]

### 2020-11-25 profiler_out/scripts/hylaa_viz_node.py

@@ -1,0 +1,106 @@
+#!/usr/bin/python
+#node to display reachsets as filled planes in rviz
+# subscribes to hylaa output topic
+# publishes RVIZ triangle list
+# configurable in hylaa_viz.yaml
+
+import rospy
+from osuf1_common.msg import ReachSets
+import tripy
+from visualization_msgs.msg import Marker, MarkerArray
+from geometry_msgs.msg import Pose, Point, Quaternion, Vector3
+from std_msgs.msg import Header, ColorRGBA, Duration
+from osuf1_common.msg import ReachSets
+from itertools import repeat
+
+#node to publish reachability visualization messages for viewing in rviz
+
+class Hylaa_Viz_Node:
+    def __init__(self):
+        rospy.init_node("hylaa_viz")
+
+
+        reach_sub_topic = rospy.get_param("/zono_node/reach_pub_topic", "hylaa_reach")
+        self.reachPub = rospy.Subscriber(reach_sub_topic, ReachSets, self.makeViz) 
+        sets_outline_topic = rospy.get_param("/hylaa_viz/outline_topic", "hylaa_viz_outline")
+        sets_tris_topic = rospy.get_param("/hylaa_viz/tris_topic", "hylaa_viz_tris")
+
+        self.outlinePub = rospy.Publisher(sets_outline_topic, MarkerArray, queue_size=100)
+        self.trisPub = rospy.Publisher(sets_tris_topic, Marker, queue_size=1)
+
+        self.tri_marker_id = 44
+        self.outline_marker_id = 555 # + n
+
+        self.colors = [(230, 25, 75), (60, 180, 75), (255, 225, 25), (0, 130, 200), (245, 130, 48), (145, 30, 180), (70, 240, 240), (240, 50, 230), (210, 245, 60), (250, 190, 190), (0, 128, 128), (230, 190, 255), (170, 110, 40), (255, 250, 200), (128, 0, 0), (170, 255, 195), (128, 128, 0), (255, 215, 180), (0, 0, 128), (128, 128, 128)]
+        self.colors = [ColorRGBA(c[0], c[1], c[2], 1) for c in self.colors]
+
+        self.skipfreq=2
+        self.skipcount=0
+
+    def start(self):
+        rospy.spin()
+    
+    def makeViz(self, reachSets):
+#        if self.skipfreq == self.skipcount:
+#            self.skipcount = 0
+#        self.skipcount += 1
+        pointSets = [[tuple(p.p) for p in rs.set] for rs in reachSets.sets]
[…]

### 2020-11-25 profiler_out/scripts/model.py

@@ -1,0 +1,85 @@
+from sympy import sin, cos, tan, Matrix, BlockMatrix, eye, zeros, pprint
+
+#model representing the linearized dynamics 
+# and bounds of a system 
+# for use with hylaa
+
+# WHY
+# ++
+#abstracting this makes it easier to test different dynamics models 
+# through rospy settings integration
+# --
+# makes it slightly more difficult to add additional dynamics fields or matrices
+#  for use in reachability algorithm
+
+
+class Model:
+    def __init__(self, symbols, constants, A_jac, B_jac, bounds_rhs):
+        self.symbols = symbols
+        self.constants = constants
+        self.A = A_jac
+        self.B = B_jac
+
+        #augment A, B for time triggered transitions
+        self.augmentDynamics() #comment for quickzono
+
+        self.bounds_rhs = bounds_rhs
+        self.bounds_mat = self.standardBounds()
+        self.invariant_mat = self.standardTimeInvariant()
+        self.guard_mat = self.standardGuard()
+        self.input_uncertainty = [0] * self.B.shape[1]
+        
+
+    def standardBounds(self):
+        a = [eye(self.B.shape[1]), -1 * eye(self.B.shape[1])]
+        a = [ai.tolist() for ai in a]
+        m = [a[p%2][p//2] for p in range(self.B.shape[1]*2)]
+        return Matrix(m)
+
+    def standardTimeInvariant(self):
+        inv = zeros(1, self.A.shape[0])
+        inv[self.A.shape[0] - 2] = 1
+        return inv
+    
+    def standardGuard(self):
+        guard =  self.invariant_mat * -1
+        return guard
+
+    def setInputUncertainty(self, input_uncertainty):
+        assert(len(input_uncertainty) == len(self.input_uncertainty))
+        self.input_uncertainty = input_uncertainty
+
+    #augment dynamics with row/col for time + time accumulation
+    def augmentDynamics(self):
+        a = self.A
+        arow = lambda : a.shape[0]
+        acol = lambda : a.shape[1]
+        b = self.B
+        brow = lambda : b.shape[0]
+        bcol = lambda : b.shape[1]
+
+        #insert two columns of 0's
+        a = a.col_insert(acol(), Matrix([0] * arow()))
+        a = a.col_insert(acol(), Matrix([0] * arow()))
+        #insert row with trailing one (time) and of 0's (time augment)
[…]

### 2020-11-25 profiler_out/scripts/model_hardcode.py

@@ -1,0 +1,64 @@
+import math
+
+#model representing the linearized dynamics 
+# and bounds of a system 
+# for use with hylaa
+
+# WHY
+# ++
+#abstracting this makes it easier to test different dynamics models 
+# through rospy settings integration
+# --
+# makes it slightly more difficult to add additional dynamics fields or matrices
+#  for use in reachability algorithm
+
+
+class Model:
+    def __init__(self):
+        self.constants = [.32, 1]
+        self.input_uncertainty = [0] * 2
+    
+    def setInputUncertainty(self, input_uncertainty):
+        print(input_uncertainty)
+        assert(len(input_uncertainty) == len(self.input_uncertainty))
+        self.input_uncertainty = input_uncertainty
+
+    def linearized_dynamics(self, state, inputs, dt):
+        #current = state+inputs+self.constants+[dt]+self.input_uncertainty
+        x, y, p = (val for val in state)
+        v, d,  = (val for val in inputs)
+        L, d0 = (val for val in self.constants)
+        # i1, i2 = input_uncertainty[1](val for val in self.input_uncertainty)
+        p_d = p + d
+        sin_p_d = math.sin(p_d)
+        cos_p_d = math.cos(p_d)
+        #sin_p_d = math.sin(p_d)
+        #cos_p_d = math.cos(p_d)
+        sin_d = math.sin(d)
+        cos_d = math.cos(d)
+
+        A = [
+            [0, 0, -v*sin_p_d, d*v*sin_p_d + p*v*sin_p_d, 0, 0],
+            [0, 0, v*cos_p_d, 0, -d*v*cos_p_d - p*v*cos_p_d, 0],
+            [0, 0, 0, 0, 0, -d*v*cos_d/L],
+            [0, 0, 0, 0, 0, 0],
+            [0, 0, 0, 0, 0, 0],
+            [0, 0, 0, 0, 0, 0]
+        ]
+
+        B = [
+            [cos_p_d, -v*sin_p_d],
+            [sin_p_d, v*cos_p_d],
+            [sin_d/L, v*cos_d/L],
+            [0, 0],
+            [0, 0],
+            [0, 0]
+        ]
+        return {
+            "A" : A,
+            "B" : B
+        }
+
+
+def getModel():
+    return Model()

### 2020-11-25 profiler_out/scripts/mpc_sim.py

@@ -1,0 +1,92 @@
+#!/usr/bin/python
+#ROS imports
+
+import rospy
+from osuf1_common.msg import MPC_metadata, MPC_trajectory, MPC_prediction
+from std_msgs.msg import Header
+from geometry_msgs.msg import PoseStamped
+from tf.transformations import euler_from_quaternion
+
+#local imports
+from nl_dynamics import F1Dynamics
+import simulator
+
+#python lib imports
+from functools import partial
+import math
+import time
+
+class MPC_Sim:
+    def __init__(self):
+
+        rospy.init_node("mpc_sim_node")
+        
+        self.nlDynamics = F1Dynamics()
+        self.stepFunc = partial(self.nlDynamics.frontStep, self.nlDynamics)
+        self.dt = rospy.get_param("/mpc_sim/dt", .1)
+        self.totalTime = rospy.get_param("/mpc_sim/total_time", 1)
+
+        self.currentState = [0, 0, 0]
+        self.inputFunc = lambda et, t : [ 4, -1 * math.cos(2*t+et)/4]
+
+#        self.simulator = simulator.ModelSimulator(self.dt, self.totalTime, self.currentState, self.stepFunc, self.inputFunc, True)
+
+        self.simulation_period = 100 #ms between publish events
+        self.prediction_pub_topic = rospy.get_param("/hylaa_node/mpc_prediction_topic", "mpc_prediction")
+        self.meta_pub_topic = rospy.get_param("/hylaa_node/mpc_metadata_topic", "mpc_metadata")
+        self.position_topic = rospy.get_param("/hylaa_node/localization_topic", "pf_pose")
+
+        self.prediction_pub = rospy.Publisher(self.prediction_pub_topic, MPC_trajectory, queue_size=1)
+        self.meta_pub = rospy.Publisher(self.meta_pub_topic, MPC_metadata, queue_size=1)
+        self.position_sub = rospy.Subscriber(self.position_topic, PoseStamped, self.parseState)
+
+        self.elapsedTime = 0
+        
+
+    def start(self):
+        rate = rospy.Rate(1000/self.simulation_period)
+        time.sleep(2)
+        while not rospy.is_shutdown():
+            results = self.simulate()
+            self.currentState = results[-1][0]
+
+            header = Header()
+            header.stamp = rospy.Time.now()
+            header.frame_id = "map"
+
+            #metadata message
+            meta = MPC_metadata()
+            meta.header = header
+            meta.dt = self.dt
+            meta.horizon = self.totalTime
[…]

### 2020-11-25 profiler_out/scripts/offline_profiler.py

@@ -1,0 +1,82 @@
+from matplotlib import pyplot as plt
+import numpy as np
+from nl_dynamics import F1Dynamics
+from functools import partial
+import math
+import time
+from timeit import Timer
+from run_f1zono import run_quickzono_CPU, run_quickzono_CPU_MP, run_quickzono_GPU_HYBRID, run_quickzono_GPU_DUMMY
+from run_f1hylaa import run_hylaa_profile
+from quickzonoreach.zono_projection import ZP_TYPE
+import pstats
+import statistics
+
+
+min_steps = 4
+max_steps = 26
+
+#steps_list = list(range(min_steps, 16)) + list(range(20, max_steps, 5))
+steps_list = list(range(min_steps, max_steps, 2))
+
+#start_steps = 9
+#end_steps = 20
+#steps_list = steps_list[steps_list.index(start_steps):steps_list.index(end_steps)]
+
+#define and store model functions
+qz_cpu = run_quickzono_CPU
+qz_mp = run_quickzono_CPU_MP 
+qz_hybrid = run_quickzono_GPU_HYBRID
+qz_dummy = run_quickzono_GPU_DUMMY
+hylaa = run_hylaa_profile
+
+all_modes = [qz_cpu, qz_mp, qz_hybrid, qz_dummy, hylaa]
+all_modes_names = ["QZ_CPU", "QZ_MP", "QZ_HYBRID", "QZ_DUMMY", "HYLAA"]
+all_modes_trials = [200, 200, 200, 200, 20]
+#all_modes_trials = [20, 20, 20, 20, 1]
+
+
+trials_per_stepsmode = 200
+full_maxtime = 0
+verts_maxtime = 0
+std_maxtime = 0
+data = [] # (time, steps, mode, verts?)
+cutoff_modes = set()
+cutoff_time = 1.5 #we only run a few trials for modes over this
+cutoff_trials = 5 #run way fewer trials once timout is reached
+
+
+inline_out = open("raw/offline_tmp.csv", "w+")
+for steps in steps_list:
+    dt = 1
+    ttime = steps
+    print("Calling for steps={}".format(steps))
+    for num, mode, name, trials in zip(range(len(all_modes)), all_modes, all_modes_names, all_modes_trials):
+        print("\tRunning {}".format(name))
+        run_trials = trials
+        if name in cutoff_modes:
+            run_trials = cutoff_trials
+        for trial in range(run_trials):
+            full_time = mode(dt, ttime, [0, 0, 0])
[…]

### 2020-11-25 profiler_out/scripts/profiler_unified.py

@@ -1,0 +1,112 @@
+
+from matplotlib import pyplot as plt
+import numpy as np
+from nl_dynamics import F1Dynamics
+from functools import partial
+import math
+import time
+from timeit import Timer
+from run_f1zono import run_quickzono_CPU, run_quickzono_CPU_MP, run_quickzono_GPU_HYBRID
+#from run_f1hylaa import run_hylaa
+from quickzonoreach.zono_projection import ZP_TYPE
+import pstats
+import statistics
+
+
+min_steps = 5
+max_steps = 40
+
+steps_list = list(range(min_steps, 16)) + list(range(20, max_steps, 5))
+
+#define and store model functions
+#hylaa = run_hylaa_profile
+qz_cpu = run_quickzono_CPU
+qz_mp = run_quickzono_CPU_MP 
+qz_hybrid = run_quickzono_GPU_HYBRID
+
+all_modes = [qz_cpu, qz_mp, qz_hybrid]
+all_modes_names = ["QZ-CPU", "QZ-MP", "QZ-HYBRID"]
+
+
+full_mode_results_avg = [[] for _ in range(len(all_modes))]
+verts_mode_results_avg = [[] for _ in range(len(all_modes))]
+full_mode_results_std = [[] for _ in range(len(all_modes))]
+verts_mode_results_std = [[] for _ in range(len(all_modes))]
+
+
+trials_per_stepsmode = 75
+full_maxtime = 0
+verts_maxtime = 0
+std_maxtime = 0
+for steps in steps_list:
+    dt = 1
+    ttime = steps
+    print("Calling for steps={}".format(steps))
+    for num, mode, name in zip(range(len(all_modes)), all_modes, all_modes_names):
+        print("\tRunning {}".format(name))
+        full_steps_results = []
+        verts_steps_results = []
+        for trial in range(trials_per_stepsmode):
+            full_time = mode(dt, ttime, [0, 0, 0])
+            verts_time = mode(dt, ttime, [0, 0, 0], profile=2)
+            verts_time = verts_time/full_time
+            if full_time > full_maxtime:
+                full_maxtime = full_time
+            if verts_time > verts_maxtime:
+                verts_maxtime = verts_time
+            full_steps_results.append(full_time)
+            verts_steps_results.append(verts_time)
+        full_mode_results_avg[num].append(np.mean(full_steps_results))
+        verts_mode_results_avg[num].append(np.mean(verts_steps_results))
[…]

### 2020-11-25 profiler_out/scripts/profiler_zono.py

@@ -1,0 +1,130 @@
+from matplotlib import pyplot as plt
+import numpy as np
+from nl_dynamics import F1Dynamics
+from functools import partial
+import math
+import time
+from timeit import Timer
+from run_f1zono import run_quickzono
+import pstats
+
+
+#TODO graph timing only for zono projections
+
+linear = lambda mini, maxi, frac : mini + (maxi - mini) * frac
+
+numDataTrials = 4
+
+#dt config
+dt_Min = .01
+dt_Max = .15
+dt_numSteps = 5
+dt_StepFunc = linear
+dt_Steps = [dt_StepFunc(dt_Min, dt_Max, step/(dt_numSteps)) for step in range(dt_numSteps)]
+print("DT steps are:")
+print(dt_Steps)
+
+#total time config
+ttime_Min = .5
+ttime_Max = 1
+ttime_numSteps = 2
+ttime_StepFunc = linear
+ttime_Steps = [ttime_StepFunc(ttime_Min, ttime_Max, step/(ttime_numSteps)) for step in range(ttime_numSteps)]
+print("Total Time Steps are")
+print(ttime_Steps)
+
+#tuple result pairs (ttime, dt, runtime)
+def printResult(r):
+    print("\033[0;32;40m Run complete with: runtime avg={}\n".format(r[2]))
+
+results = []
+
+maxSimSteps = 50
+#testing on dt and total
+for totalTime in ttime_Steps:
+    print("-----------------------------------")
+    print("\033[0;32;40m Running time series with: ttime={}\033[0;37;40m".format(totalTime))
+    print("-----------------------------------")
+    step_results = []
+    for dt in dt_Steps:
+        if totalTime / dt < maxSimSteps:
+            print("\033[0;32;40m Running model with : ttime={}, dt={}\033[0;37;40m".format(totalTime, dt))
+            stamp = "{}{}".format(totalTime, dt).replace('.','d')
+            runTimeTrials = []
+            print("Trials completed... \n", end='')
+            for t in range(numDataTrials):
+                print("{}".format(t+1), end=' ')
+                runTimeTrials.append(run_quickzono(dt, totalTime, [0, 0, 0], True))
+
+            #with open('profiler/raw/profile_out_{}_{}.txt'.format(dt*1000,totalTime), 'w+') as stream:
[…]

### 2020-11-25 profiler_out/scripts/run_f1hylaa.py

@@ -1,0 +1,60 @@
+#barebones testing script to run hylaa without ROS
+# also used by profiler
+
+from F1Hylaa import F1Hylaa
+#local imports
+from nl_dynamics import F1Dynamics
+import simulator
+
+#python lib imports
+from functools import partial
+import math
+import time
+import xmlrpc.client
+from timeit import Timer
+
+state_uncertainty = [.1, .1, 0]
+input_uncertainty = [.1, 3.14/90] # .1m/s , 2deg
+nlDynamics = F1Dynamics()
+stepFunc = partial(nlDynamics.frontStep, nlDynamics)
+inputFunc = lambda t : [ 1+4, -1 * math.cos(2)/4]
+headless = True
+fy = F1Hylaa()
+
+def run_hylaa_profile(dt, ttime, initialState = [0, 0, 0]):
+    return run_hylaa(dt, ttime, initialState, True, False)
+
+def run_hylaa(dt, ttime, initialState, do_profile=False, output=False):
+    sim = simulator.ModelSimulator(dt, ttime, initialState, stepFunc, inputFunc, headless)
+
+    print("Simulating")
+    global predictions
+    predictions = sim.simulate()
+    print("Simulation Finished, Initializing Reachability")
+
+
+    fy.set_model_params(state_uncertainty, input_uncertainty, "kinematics_model")
+    fy.make_settings(dt, ttime, output, "VERBOSE", "hylaa.png")
+
+    print("Running HYLAA")
+    result = None
+    if do_profile:
+        timer = Timer("""fy.run_hylaa(predictions)""", globals=globals())
+        result = timer.timeit(1)
+    else:
+        result = fy.run_hylaa(predictions)
+    print("HYLAA execution finished.")
+    #print(result)
+    #print("Stateset obj")
+    #print(result[0][-3])
+    return result
+
+
+if __name__ == "__main__":
+    print("Initializing Simulation")
+    initialState = [0, 0, 0]
+    dt = .05
+    ttime = 1
+    output = "IMAGE"
+    reach = run_hylaa(dt, ttime, initialState, output)
+

### 2020-11-25 profiler_out/scripts/run_f1zono.py

@@ -1,0 +1,132 @@
+#!/home/dev/cuda-venv/bin/python3
+
+#barebones testing script to run reachability without ROS
+# also used by profiler
+
+from F1QuickZono import F1QuickZono
+
+#local imports
+from nl_dynamics import F1Dynamics
+import simulator
+
+#python lib imports
+from functools import partial
+import math
+import time
+
+import matplotlib.pyplot as plt
+import cProfile as profile
+
+#from pycallgraph import PyCallGraph
+#from pycallgraph.output import GraphvizOutput
+from timeit import Timer
+import numpy as np
+import sys
+
+gen_callgraph = False
+if gen_callgraph:
+    from pycallgraph import PyCallGraph
+    from pycallgraph import Config
+    from pycallgraph.output import GraphvizOutput
+
+state_uncertainty = [.05, .1, 0]
+input_uncertainty = [.2, 3.14/90] # .1m/s , 2deg
+nlDynamics = F1Dynamics()
+stepFunc = partial(nlDynamics.frontStep, nlDynamics)
+inputFunc = lambda t : [ 3 * t, 2 * math.sin(3.14 * t)/2]
+headless = True
+
+#modal wrappers for profiler
+def run_quickzono_CPU(dt, ttime, initialState, profile=1):
+    return run_quickzono(dt, ttime, initialState, profile, "CPU")
+
+def run_quickzono_CPU_MP(dt, ttime, initialState, profile=1):
+    return run_quickzono(dt, ttime, initialState, profile, "CPU_MP")
+
+def run_quickzono_GPU_HYBRID(dt, ttime, initialState, profile=1):
+    return run_quickzono(dt, ttime, initialState, profile, "GPU_HYBRID")
+
+def run_quickzono_GPU_DUMMY(dt, ttime, initialState, profile=1):
+    return run_quickzono(dt, ttime, initialState, profile, "GPU_DUMMY")
+
+def run_quickzono(dt, ttime, initialState, do_profile=0, runtime_mode="GPU_HYBRID"):
+    fy = F1QuickZono() 
+    fy.set_model_params(state_uncertainty, input_uncertainty, "model_hardcode", runtime_mode=runtime_mode)
+    sim = simulator.ModelSimulator(dt, ttime, initialState, stepFunc, inputFunc, headless)
+
+    #print("Simulating")
+    predictions = sim.simulate()
+    #print("Simulation Finished, Initializing Reachability")
+
[…]

### 2020-11-25 profiler_out/scripts/simulator.py

@@ -1,0 +1,66 @@
+import math
+
+#simulator for generating state approximations of nonlinear model
+# --used to create approximation used to initialize HYLAA states
+# stepFunc is as follows: (state can be any type, input must agree with inputfunc)
+
+def exampleStepFunc(state, input):
+    state[0] = state[0]
+
+    return state
+
+#inputfunc is as follows:
+
+def exampleInputFunc(time):
+    return math.cos(time) * 5 #constant modulation for this example
+
+class ModelSimulator():
+
+    def __init__(self, dt, totalTime, initialState, stepFunc=None, inputFunc=None, headless=False):
+        self.dt = dt
+        self.totalTime = totalTime
+        assert dt < totalTime, "dt >= total time - undefined configuration"
+
+        self.stepFunc = stepFunc
+        self.inputFunc = inputFunc
+        self.currentState = initialState
+
+        self.verbose = not headless
+    
+    def simulate(self, stepFunc=None, inputFunc=None):
+        if stepFunc:
+            self.stepFunc = stepFunc
+        assert self.stepFunc != None , "Step Function must be specified"
+
+        if inputFunc:
+            self.inputFunc = inputFunc 
+        assert self.inputFunc != None , "Input Function must be specified"
+
+        time = 0
+        steps = int(self.totalTime / self.dt)
+
+        if self.verbose:
+            print("Simulating {} steps with dt={}".format(steps, self.dt))
+
+        #this will store all the generated states
+        self.stateList = [(self.currentState, self.inputFunc(time))]
+
+        if self.verbose:
+            print("Initial state at time {}: \n\t{}".format(time, self.stateList[-1]))
+
+        for step in range(steps):
+            time += self.dt
+            inputs = self.inputFunc(time)
+
+            self.currentState = self.stepFunc(self.currentState, inputs, self.dt)
+            self.stateList.append((
+                self.currentState,
+                inputs
+            ))
+            
+            if self.verbose:
+                print("Step {} at time {}: \n\t{}".format(step+1, time, self.stateList[-1]))
+        
+        return self.stateList
+
+

### 2020-11-25 profiler_out/scripts/zono_node.py

@@ -1,0 +1,190 @@
+#!/usr/bin/python3.6
+# library imports
+from functools import partial
+
+#local imports
+from F1QuickZono import F1QuickZono
+
+#ROS imports
+import rospy
+from std_msgs.msg import Header
+from osuf1_common.msg import MPC_trajectory, MPC_metadata, MPC_prediction, ReachSets, NPointSet, NPoint
+import time
+
+#convenience map for outputing matching mode names from online and offline profiling
+mode_format = {
+    "CPU" : "QZ_CPU",
+    "CPU_MP" : "QZ_MP",
+    "GPU_HYBRID" : "QZ_HYBRID",
+    "GPU_DUMMY" : "QZ_DUMMY",
+    "GPU" : "QZ_GPU",
+    "HYLAA" : "HYLAA"
+}
+
+class ZONO_Node:
+    def __init__(self):
+
+        rospy.init_node("zono_node")
+
+        #self.modeList = None    #store list of all modes so we can retrieve correct reachsets
+        #self.initialBox = None  #we need to store the initial stateset
+        #self.core = None        #core object for running hylaa with settings
+
+        #---------------------------------------------------------
+        #                   REACHABILITY Params
+        #---------------------------------------------------------
+        self.predictions = None #predictions from MPC
+        self.reachability_horizon = rospy.get_param("zono_node/horizon", 0)
+        self.runtime_mode = rospy.get_param("zono_node/runtime_mode", "CPU")
+        self.dt = None          #dt from MPC metdata
+        self.mpc_horizon = None #simulation horizon from MPC metadata
+
+        #TODO automatic or otherwise validated variability
+        self.state_uncertainty = [
+            rospy.get_param("zono_node/state_uncertainty/px", 0),
+            rospy.get_param("zono_node/state_uncertainty/py", 0),
+            rospy.get_param("zono_node/state_uncertainty/psi", 0),
+        ]
+        rospy.loginfo(self.state_uncertainty)
+
+        self.input_uncertainty = [
+            rospy.get_param("zono_node/input_uncertainty/velocity", 0),
+            rospy.get_param("zono_node/input_uncertainty/delta", 0)
+        ]
+
+
+        #custom horizon or utilize all computed MPC steps
+        self.hylaa_verbosity = rospy.get_param("zono_node/output_verbosity", "VERBOSE").upper() #TODO integrate with roslogger 
[…]

### 2020-11-25 copy_media.sh
actually upload new graphs

@@ -1,1 +1,1 @@
-cp -r /home/dev/cuda-venv/src/ppcm/reachability/scripts ./profiler_out
+cp -r /home/dev/cuda-venv/src/ppcm/reachability/scripts/profiler ./profiler_out

### 2020-11-25 profiler_out/scripts/F1Hylaa.py

@@ -1,225 +1,0 @@
-# library imports
-from functools import partial
-from scipy.io import loadmat
-import importlib
-
-#hylaa imports
-from hylaa.hybrid_automaton import HybridAutomaton 
-from hylaa.settings import HylaaSettings, PlotSettings, LabelSettings 
-from hylaa.core import Core
-from hylaa.stateset import StateSet
-from hylaa import lputil
-from matplotlib.patches import Circle, Ellipse
-from matplotlib import collections
-from matplotlib import pyplot as plt
-
-#local imports
-from nl_dynamics import F1Dynamics
-import simulator
-
-##ROS imports
-#import rospy
-#from osuf1_common import StampedFloat2d, MPC_metadata
-#from profilehooks import profile
-import cProfile as profile
-
-#wrapper to run hylaa repeatedly with different inputs
-class F1Hylaa:
-    def __init__(self):
-
-        # ------------------ Semi-Static Configuration ----------------------
-        self.settings = None #hylaa settings object
-        self.dt = None          #dt from MPC metdata
-        self.ttime = None
-
-        self.input_uncertainty = []
-        self.state_uncertainty = []
-
-        self.model = None       #dynamics abstraction object
-
-        #TODO automatic or otherwise validated variability
-        # ------------------ Per-run Configuration ----------------------
-        self.ha = None
-        self.predictions = None #predictions from MPC 3d array : [ dt[ state[x,y,psi], inputs[d,v] ] ]
-        self.modeList = []
-        self.initialState = None
-
-
-    def set_model_params(self, state_uncertainty, input_uncertainty, dynamics_module="kinematics_model"):
-        model_gen = importlib.import_module(dynamics_module)
-        self.modeList = []
-        self.state_uncertainty = state_uncertainty
-        self.input_uncertainty = input_uncertainty
-        self.model = model_gen.getModel()
-        self.model.setInputUncertainty(input_uncertainty)
-
-        return 1
-    
-    def run_hylaa(self, predictions):
-        self.ha = None
-        self.predictions = None
-        self.modeList = []
-        self.initialState = None
-
-        self.ha = HybridAutomaton()
-        self.predictions = predictions
-        self.graphPredictions()
-        self.make_automaton()
-
-        initialBox = self.make_init(self.predictions[0][0])
-        core = Core(self.ha, self.settings)
[…]

### 2020-11-25 profiler_out/scripts/F1QuickZono.py

@@ -1,138 +1,0 @@
-# library imports
-from functools import partial
-import importlib
-#from concurrent.futures import ThreadPoolExecutor, ProcessPoolExecutor
-#import dill
-from multiprocessing import Pool
-
-#local imports
-from nl_dynamics import F1Dynamics
-
-from quickzonoreach.zono import get_zonotope_reachset
-from quickzonoreach.zono_projection import ZP_TYPE, get_ZP_instance
-
-#wrapper to run quickzono repeatedly with different inputs
-class F1QuickZono:
-    def __init__(self):
-
-        # ------------------ Semi-Static Configuration ----------------------
-        self.dt = None          #dt from MPC metdata
-        self.ttime = None
-        self.num_steps = None
-
-        self.input_uncertainty = []
-        self.state_uncertainty = []
-
-        self.model = None       #dynamics abstraction object
-
-        #TODO automatic or otherwise validated variability
-        # ------------------ Per-run Configuration ----------------------
-        self.predictions = None #predictions from MPC 3d array : [ dt[ state[x,y,psi], inputs[d,v] ] ]
-
-        self.init_box = []
-        self.a_mat_list = []
-        self.b_mat_list = []
-        self.input_box_list = []
-        self.dt_list = []
-        self.save_list = []
-
-
-        self.ZP = None 
-
-
-    def set_model_params(self, state_uncertainty, input_uncertainty, dynamics_module="kinematics_model", runtime_mode="CPU"):
-        model_gen = importlib.import_module(dynamics_module)
-        self.modeList = []
-        self.state_uncertainty = state_uncertainty
-        self.input_uncertainty = input_uncertainty
-        self.model = model_gen.getModel()
-        self.model.setInputUncertainty(input_uncertainty)
-        
-        
-        self.ZP = get_ZP_instance(ZP_TYPE[runtime_mode])
-        return 1
-    
-    def run(self, predictions, profile=False):
-        self.predictions = predictions[:self.num_steps]
-
-        self.quick = True
-        self.a_mat_list = []
-        self.b_mat_list = []
-        self.input_box_list = []
-
-
-        #profile.runctx('resultprof = self.run_zono(initialBox, core)', globals(), locals(), filename="profiler/prof/out_tmp.prof")
-        #result = locals()['resultprof']
-        self.make_dynamics()
-        self.make_init(self.predictions[0][0])
-        zonos = self.run_zono()
-
-
-        #do projection for safety analysis in 2d
-        if profile:
[…]

### 2020-11-25 profiler_out/scripts/debug_sudo.sh

@@ -1,3 +1,0 @@
-. ~/cuda-venv/bin/activate;
-export PYTHONPATH=/home/dev/cuda-venv/src:$PYTHONPATH
-cuda-gdb --args python3 -m pycuda.debug run_f1zono.py

### 2020-11-25 profiler_out/scripts/graph_maker.py

@@ -1,281 +1,0 @@
-import pandas as pd
-import scipy.stats
-import matplotlib.pyplot as plt
-import numpy as np
-
-import scipy.stats as st
-def get_best_distribution(data):
-    dist_names = ["norm", "exponweib", "weibull_max", "weibull_min", "pareto", "genextreme"]
-    dist_results = []
-    params = {}
-    for dist_name in dist_names:
-        dist = getattr(st, dist_name)
-        param = dist.fit(data)
-
-        params[dist_name] = param
-        # Applying the Kolmogorov-Smirnov test
-        D, p = st.kstest(data, dist_name, args=param)
-        dist_results.append((dist_name, p))
-
-    # select the best fitted distribution
-    best_dist, best_p = (max(dist_results, key=lambda item: item[1]))
-    # store the name of the best fit and its p value
-
-    print("Best fitting distribution: "+str(best_dist))
-    print("Best p value: "+ str(best_p))
-    #print("Parameters for the best fit: "+ str(params[best_dist]))
-
-    return best_dist, best_p, params[best_dist]
-
-upstatus = "Offline"
-csv_input = "raw/offline_FINAL.csv"
-csv_input_2 = "raw/online_FINAL.csv"
-
-
-import pdb
-columns = ["time", "steps", "mode", "verts"]
-timing_data = pd.read_csv(csv_input, sep=",", names=columns) 
-timing_data["env"] = pd.Series(["offline"] * len(timing_data), index=timing_data.index)
-timing_data_2 = pd.read_csv(csv_input_2, sep=",", names=columns)
-timing_data_2["env"] = pd.Series(["online"] * len(timing_data_2), index=timing_data_2.index)
-timing_data = pd.concat([timing_data, timing_data_2])
-
-
-
-print(timing_data[:6])
-
-modes = list(timing_data['mode'].unique())
-modes.remove("HYLAA")
-online_steps = timing_data.loc[timing_data['env']=="online"]['steps'].unique()
-offline_steps = timing_data.loc[timing_data['env']=="offline"]['steps'].unique()
-steps = offline_steps
-online_steps = [s for s in online_steps if s in offline_steps]
-envs = timing_data['env'].unique()
-conf_interval_prop = .95
-
-timing_stats = pd.DataFrame(
[…]

### 2020-11-25 profiler_out/scripts/hylaa_node.py

@@ -1,136 +1,0 @@
-#!/usr/bin/python3.6
-# library imports
-from functools import partial
-
-#local imports
-from F1Hylaa import F1Hylaa
-
-#ROS imports
-import rospy
-from std_msgs.msg import Header
-from osuf1_common.msg import MPC_trajectory, MPC_metadata, MPC_prediction, ReachSets, NPointSet, NPoint
-
-class HYLAA_node:
-    def __init__(self):
-
-        rospy.init_node("hylaa_node")
-
-        #self.modeList = None    #store list of all modes so we can retrieve correct reachsets
-        #self.initialBox = None  #we need to store the initial stateset
-        #self.core = None        #core object for running hylaa with settings
-
-        #---------------------------------------------------------
-        #                   HYLAA Params
-        #---------------------------------------------------------
-        self.predictions = None #predictions from MPC
-        self.reachability_horizon = rospy.get_param("/hylaa_node/horizon", 0)
-        self.dt = None          #dt from MPC metdata
-        self.mpc_horizon = None #simulation horizon from MPC metadata
-
-        #TODO automatic or otherwise validated variability
-        self.state_uncertainty = [
-            rospy.get_param("/hylaa_node/state_uncertainty/px", 0),
-            rospy.get_param("/hylaa_node/state_uncertainty/py", 0),
-            rospy.get_param("/hylaa_node/state_uncertainty/psi", 0),
-        ]
-
-        self.input_uncertainty = [
-            rospy.get_param("/hylaa_node/input_uncertainty/velocity", 0),
-            rospy.get_param("/hylaa_node/input_uncertainty/delta", 0)
-        ]
-
-
-        #custom horizon or utilize all computed MPC steps
-        self.hylaa_verbosity = rospy.get_param("/hylaa_node/output_verbosity", "VERBOSE").upper() #TODO integrate with roslogger 
-        self.graph_predictions = rospy.get_param("/hylaa_node/graph_predictions", False) #wether predicted sim results should be overlayed on reach set graph (if displayed)
-        self.displayType = rospy.get_param("/hylaa_node/display_type", "NONE").upper()
-        self.output = rospy.get_param("/hylaa_node/display_filename", "hylaa_reach.png") #TODO put images in distinct folder and label with frame times
-
-
-        #---------------------------------------------------------
-        #                   HYLAA Calling Vars
-        #---------------------------------------------------------
-        self.hylaa = F1Hylaa()
[…]

### 2020-11-25 profiler_out/scripts/hylaa_viz_node.py

@@ -1,106 +1,0 @@
-#!/usr/bin/python
-#node to display reachsets as filled planes in rviz
-# subscribes to hylaa output topic
-# publishes RVIZ triangle list
-# configurable in hylaa_viz.yaml
-
-import rospy
-from osuf1_common.msg import ReachSets
-import tripy
-from visualization_msgs.msg import Marker, MarkerArray
-from geometry_msgs.msg import Pose, Point, Quaternion, Vector3
-from std_msgs.msg import Header, ColorRGBA, Duration
-from osuf1_common.msg import ReachSets
-from itertools import repeat
-
-#node to publish reachability visualization messages for viewing in rviz
-
-class Hylaa_Viz_Node:
-    def __init__(self):
-        rospy.init_node("hylaa_viz")
-
-
-        reach_sub_topic = rospy.get_param("/zono_node/reach_pub_topic", "hylaa_reach")
-        self.reachPub = rospy.Subscriber(reach_sub_topic, ReachSets, self.makeViz) 
-        sets_outline_topic = rospy.get_param("/hylaa_viz/outline_topic", "hylaa_viz_outline")
-        sets_tris_topic = rospy.get_param("/hylaa_viz/tris_topic", "hylaa_viz_tris")
-
-        self.outlinePub = rospy.Publisher(sets_outline_topic, MarkerArray, queue_size=100)
-        self.trisPub = rospy.Publisher(sets_tris_topic, Marker, queue_size=1)
-
-        self.tri_marker_id = 44
-        self.outline_marker_id = 555 # + n
-
-        self.colors = [(230, 25, 75), (60, 180, 75), (255, 225, 25), (0, 130, 200), (245, 130, 48), (145, 30, 180), (70, 240, 240), (240, 50, 230), (210, 245, 60), (250, 190, 190), (0, 128, 128), (230, 190, 255), (170, 110, 40), (255, 250, 200), (128, 0, 0), (170, 255, 195), (128, 128, 0), (255, 215, 180), (0, 0, 128), (128, 128, 128)]
-        self.colors = [ColorRGBA(c[0], c[1], c[2], 1) for c in self.colors]
-
-        self.skipfreq=2
-        self.skipcount=0
-
-    def start(self):
-        rospy.spin()
-    
-    def makeViz(self, reachSets):
-#        if self.skipfreq == self.skipcount:
-#            self.skipcount = 0
-#        self.skipcount += 1
-        pointSets = [[tuple(p.p) for p in rs.set] for rs in reachSets.sets]
[…]

### 2020-11-25 profiler_out/scripts/kinematics_model.py

@@ -1,85 +1,0 @@
-from model import Model
-from sympy import sin, cos, tan, Matrix, symbols, MatrixSymbol, BlockMatrix, eye, diag, zeros, pprint, init_printing
-
-def getModel():
-    # ---------- STATE (S) -----------
-    #variables
-    x, y, p = symbols('x y  p')
-    S_k = [x, y, p]
-
-
-    # ---------- INPUTS (U) -----------
-    #variables
-    v, d = symbols('v d')
-    U_k = Matrix([v, d])
-
-    # ---------- STATE LINEARIZATION (Sbar)  -----------
-    xb, yb, pb = symbols('xb yb pb')
-    Sbar = Matrix([xb, yb, pb])
-
-    # ---------- INPUT LINEARIZATION (Ubar)  -----------
-    vb, db = symbols('vb db')
-    Ubar = Matrix([vb, db])
-
-    # ---------- BOUNDS -----------
-    vs, ds = symbols('vs ds')
-    boundVars = Matrix([vs, ds])
-    bounds_rhs = Matrix([
-        vb + vs, -(vb - vs),
-        db + ds, -(db - ds)
-    ])
-
-    # ---------- CONSTANTS -----------
-    #variables
-    L, dt = symbols('L dt')
-    L0 = .32
-    constantVals = [L0]
-    constantSym = Matrix([L, dt])
-
-    # F(Sbar, UBar)
-    F = Matrix([
-        vb * cos(pb + db),
-        vb * sin(pb + db),
-        (vb/L) * sin(db)
-    ])
-
-    #find partials
-    dFdS = F.jacobian(Sbar)
-    dFdU = F.jacobian(Ubar)
-
-    #construct constant matrix
-    C = F - (dFdS * Sbar) - (dFdU * Ubar)
-
-    #define final state/inputs
-    S = S_k + [1] * C.shape[0]
-    U = U_k
-
-    #make pieces of A-matrix and combine (state dynamics)
-    M1 = dFdS  #+ eye(Sbar.shape[0])
-    M2 = diag(*C)
-    M3 = zeros(Sbar.shape[0])
-    M4 = zeros(C.shape[0])
-    
-    A_mat = Matrix(BlockMatrix([
-        [M1, M2],
-        [M3, M4]
-    ]))
-
-    #Assemble B-matrix (input dynamics)
-    B_mat =  Matrix( [
-        dFdU,
[…]

### 2020-11-25 profiler_out/scripts/kinematics_model_old.py

@@ -1,60 +1,0 @@
-from model import Model
-from sympy import sin, cos, tan, Matrix, symbols
-
-def getModel():
-    # ---------- STATE (X) -----------
-    #variables
-    x, y, p = symbols('x y p')
-    stateVars = [x, y, p]
-
-
-    # ---------- INPUT (U) -----------
-    #variables
-    v, d, e0, d0 = symbols('v d e0 d0')
-    inputVars = [v, d, e0, d0]
-
-    #bounds
-    vs, ds, e0s, d0s = symbols('vs ds e0s d0s')
-    boundVars = [vs, ds, e0s, d0s]
-    bounds_rhs = Matrix([
-        v + vs, -(v - vs),
-        d + ds, -(d - ds),
-        e0, -e0,
-        d0, -d0
-    ])
-
-    # ---------- CONSTANTS -----------
-    #variables
-    L = symbols('L')
-    L0 = .32
-    constantVals = [L0]
-    constantSym = [L]
-
-    nl_equations = Matrix([
-        v * cos(p),
-        v * sin(p),
-        (v/L) * sin(d)
-    ])
-
-
-
-    #TODO cleaner manual jacobian changes using substitution
-    #   half-working commented in model_OLD.py
-
-    #substitutions for generating proper linearizations after evaluation
-    A_jacobian = nl_equations.jacobian(stateVars)
-    B_jacobian = nl_equations.jacobian(inputVars)
-
-    matidx = lambda shape, r, c : shape[1] * r + c
-    idx_A = lambda r, c : matidx(A_jacobian.shape, r, c)
-    idx_B = lambda r, c : matidx(B_jacobian.shape, r, c)
-
-
-    B_jacobian[idx_B(0,2)] = -1 * A_jacobian[idx_A(0,2)] #e0 for x
-    B_jacobian[idx_B(1,2)] = -1 * A_jacobian[idx_A(1,2)] #e0 for y
-    B_jacobian[idx_B(0,3)] = -1 * B_jacobian[idx_B(0,1)] #d0 for x
-    B_jacobian[idx_B(1,3)] = -1 * B_jacobian[idx_B(1,1)] #d0 for y
-    B_jacobian[idx_B(2,3)] = -1 * B_jacobian[idx_B(2,1)] #d0 for e
-
-    all_vars = stateVars + inputVars + constantSym + boundVars
-    return Model(all_vars, constantVals, A_jacobian, B_jacobian, bounds_rhs)

### 2020-11-25 profiler_out/scripts/lin_dynamics.py

@@ -1,59 +1,0 @@
-from sympy import sin, cos, tan, sec, symbols, Matrix
-
-#linear dynamics represented with sympy
-class F1Dynamics_Linear:
-
-    def __init__(self, initState):
-        self.e0 = initState[2]
-        self.d0 = 0
-        self.setupEquations()
-    
-    def setupEquations(self):
-        L = .32
-        x, y, e, v, d, dt, e0, d0 = symbols("x y e v d dt e0 d0")
-        self.varSym = [x, y, e, v, d, dt, e0, d0]
-        self.frontDynamics = Matrix([
-            x + dt * v * (cos(e0+d0) - (e-e0)*sin(e0+d0)-(d-d0)*sin(d0+e0)),
-            y + dt * v * (sin(e0+d0) + (e-e0)*cos(e0+d0)+(d-d0)*cos(d0+e0)),
-            e + dt * v * (sin(d0)+(d-d0)*cos(d0)) * (1/L)
-        ])
-
-        self.rearDynamics = Matrix([
-            x + dt * v * (cos(self.e0)-(e-self.e0)*sin(self.e0)),
-            y + dt * v * (sin(self.e0)+(e-self.e0)*cos(self.e0)),
-            e + dt * (v / L) * (tan(0)+(d)*sec(0)*sec(0))
-        ])
-
-        self.hylaaDynamics = Matrix([
-            x + dt * v * (cos(e0+d0) - e*sin(e0+d0) - d * sin(e0+d0) ),
-            y + dt * v * (sin(e0 + d0) + e*cos(e0+d0) + d* cos(e0+d0)),
-            e + dt * v * (1/L) * (sin(d0) + d*cos(d0))
-        ])
-
-    def frontStep(self, caller, state, input, dt):
-        varSub = list(zip(self.varSym, state + input + [dt, self.e0, self.d0]))
-        res = list(self.frontDynamics.subs(varSub).evalf())
-        self.e0 = state[2]
-        self.d0 = input[1]
-        return res
-    
-    def rearStep(self, caller, state, input, dt):
-        varSub = list(zip(self.varSym, state + input + [dt]))
-        self.e0 = state[2]
-        return list(self.rearDynamics.subs(varSub).evalf())
-    
-    #issue #1 is out of sync initial state (e0, d0)
-    #issue #2 is flipped signs
-    #issue #3 is 
-    def hylaaStep(self, caller, state, input, dt):
[…]

### 2020-11-25 profiler_out/scripts/model.py

@@ -1,85 +1,0 @@
-from sympy import sin, cos, tan, Matrix, BlockMatrix, eye, zeros, pprint
-
-#model representing the linearized dynamics 
-# and bounds of a system 
-# for use with hylaa
-
-# WHY
-# ++
-#abstracting this makes it easier to test different dynamics models 
-# through rospy settings integration
-# --
-# makes it slightly more difficult to add additional dynamics fields or matrices
-#  for use in reachability algorithm
-
-
-class Model:
-    def __init__(self, symbols, constants, A_jac, B_jac, bounds_rhs):
-        self.symbols = symbols
-        self.constants = constants
-        self.A = A_jac
-        self.B = B_jac
-
-        #augment A, B for time triggered transitions
-        self.augmentDynamics() #comment for quickzono
-
-        self.bounds_rhs = bounds_rhs
-        self.bounds_mat = self.standardBounds()
-        self.invariant_mat = self.standardTimeInvariant()
-        self.guard_mat = self.standardGuard()
-        self.input_uncertainty = [0] * self.B.shape[1]
-        
-
-    def standardBounds(self):
-        a = [eye(self.B.shape[1]), -1 * eye(self.B.shape[1])]
-        a = [ai.tolist() for ai in a]
-        m = [a[p%2][p//2] for p in range(self.B.shape[1]*2)]
-        return Matrix(m)
-
-    def standardTimeInvariant(self):
-        inv = zeros(1, self.A.shape[0])
-        inv[self.A.shape[0] - 2] = 1
-        return inv
-    
-    def standardGuard(self):
-        guard =  self.invariant_mat * -1
-        return guard
-
-    def setInputUncertainty(self, input_uncertainty):
-        assert(len(input_uncertainty) == len(self.input_uncertainty))
-        self.input_uncertainty = input_uncertainty
-
-    #augment dynamics with row/col for time + time accumulation
-    def augmentDynamics(self):
-        a = self.A
-        arow = lambda : a.shape[0]
-        acol = lambda : a.shape[1]
-        b = self.B
-        brow = lambda : b.shape[0]
-        bcol = lambda : b.shape[1]
-
-        #insert two columns of 0's
-        a = a.col_insert(acol(), Matrix([0] * arow()))
-        a = a.col_insert(acol(), Matrix([0] * arow()))
-        #insert row with trailing one (time) and of 0's (time augment)
[…]

### 2020-11-25 profiler_out/scripts/nl_dynamics.py

@@ -1,36 +1,0 @@
-from sympy import sin, cos, tan, symbols, Matrix
-
-#nonlinear dynamics represented with sympy
-class F1Dynamics:
-    def __init__(self):
-        self.setupEquations()
-    
-    def setupEquations(self):
-        L = .32
-        x, y, e, v, d, dt = symbols("x y e v d dt")
-        self.varSym = [x, y, e, v, d, dt]
-        self.frontDynamics = Matrix([
-            x + dt * v * cos(e + d),
-            y + dt * v * sin(e + d),
-            e + dt * (v/L) * sin(d)
-        ])
-
-        self.rearDynamics = Matrix([
-            x + dt * v * cos(e + d),
-            y + dt * v * sin(e + d),
-            e + dt * (v / L) * tan(d)
-        ])
-
-    def frontStep(self, caller, state, input, dt):
-        varSub = list(zip(self.varSym, state + input + [dt]))
-        return list(self.frontDynamics.subs(varSub).evalf())
-    
-    def rearStep(self, caller, state, input, dt):
-        varSub = list(zip(self.varSym, state + input + [dt]))
-        return list(self.rearDynamics.subs(varSub).evalf())
-    
-    def getDims(self):
-        return {
-            "state" : [1, 3],
-            "input" : [1, 2]
-        }

### 2020-11-25 profiler_out/scripts/offline_profiler.py

@@ -1,82 +1,0 @@
-from matplotlib import pyplot as plt
-import numpy as np
-from nl_dynamics import F1Dynamics
-from functools import partial
-import math
-import time
-from timeit import Timer
-from run_f1zono import run_quickzono_CPU, run_quickzono_CPU_MP, run_quickzono_GPU_HYBRID, run_quickzono_GPU_DUMMY
-from run_f1hylaa import run_hylaa_profile
-from quickzonoreach.zono_projection import ZP_TYPE
-import pstats
-import statistics
-
-
-min_steps = 4
-max_steps = 26
-
-#steps_list = list(range(min_steps, 16)) + list(range(20, max_steps, 5))
-steps_list = list(range(min_steps, max_steps, 2))
-
-#start_steps = 9
-#end_steps = 20
-#steps_list = steps_list[steps_list.index(start_steps):steps_list.index(end_steps)]
-
-#define and store model functions
-qz_cpu = run_quickzono_CPU
-qz_mp = run_quickzono_CPU_MP 
-qz_hybrid = run_quickzono_GPU_HYBRID
-qz_dummy = run_quickzono_GPU_DUMMY
-hylaa = run_hylaa_profile
-
-all_modes = [qz_cpu, qz_mp, qz_hybrid, qz_dummy, hylaa]
-all_modes_names = ["QZ_CPU", "QZ_MP", "QZ_HYBRID", "QZ_DUMMY", "HYLAA"]
-all_modes_trials = [200, 200, 200, 200, 20]
-#all_modes_trials = [20, 20, 20, 20, 1]
-
-
-trials_per_stepsmode = 200
-full_maxtime = 0
-verts_maxtime = 0
-std_maxtime = 0
-data = [] # (time, steps, mode, verts?)
-cutoff_modes = set()
-cutoff_time = 1.5 #we only run a few trials for modes over this
-cutoff_trials = 5 #run way fewer trials once timout is reached
-
-
-inline_out = open("raw/offline_tmp.csv", "w+")
-for steps in steps_list:
-    dt = 1
-    ttime = steps
-    print("Calling for steps={}".format(steps))
-    for num, mode, name, trials in zip(range(len(all_modes)), all_modes, all_modes_names, all_modes_trials):
-        print("\tRunning {}".format(name))
-        run_trials = trials
-        if name in cutoff_modes:
-            run_trials = cutoff_trials
-        for trial in range(run_trials):
-            full_time = mode(dt, ttime, [0, 0, 0])
[…]

### 2020-11-25 profiler_out/scripts/profiler_unified.py

@@ -1,112 +1,0 @@
-
-from matplotlib import pyplot as plt
-import numpy as np
-from nl_dynamics import F1Dynamics
-from functools import partial
-import math
-import time
-from timeit import Timer
-from run_f1zono import run_quickzono_CPU, run_quickzono_CPU_MP, run_quickzono_GPU_HYBRID
-#from run_f1hylaa import run_hylaa
-from quickzonoreach.zono_projection import ZP_TYPE
-import pstats
-import statistics
-
-
-min_steps = 5
-max_steps = 40
-
-steps_list = list(range(min_steps, 16)) + list(range(20, max_steps, 5))
-
-#define and store model functions
-#hylaa = run_hylaa_profile
-qz_cpu = run_quickzono_CPU
-qz_mp = run_quickzono_CPU_MP 
-qz_hybrid = run_quickzono_GPU_HYBRID
-
-all_modes = [qz_cpu, qz_mp, qz_hybrid]
-all_modes_names = ["QZ-CPU", "QZ-MP", "QZ-HYBRID"]
-
-
-full_mode_results_avg = [[] for _ in range(len(all_modes))]
-verts_mode_results_avg = [[] for _ in range(len(all_modes))]
-full_mode_results_std = [[] for _ in range(len(all_modes))]
-verts_mode_results_std = [[] for _ in range(len(all_modes))]
-
-
-trials_per_stepsmode = 75
-full_maxtime = 0
-verts_maxtime = 0
-std_maxtime = 0
-for steps in steps_list:
-    dt = 1
-    ttime = steps
-    print("Calling for steps={}".format(steps))
-    for num, mode, name in zip(range(len(all_modes)), all_modes, all_modes_names):
-        print("\tRunning {}".format(name))
-        full_steps_results = []
-        verts_steps_results = []
-        for trial in range(trials_per_stepsmode):
-            full_time = mode(dt, ttime, [0, 0, 0])
-            verts_time = mode(dt, ttime, [0, 0, 0], profile=2)
-            verts_time = verts_time/full_time
-            if full_time > full_maxtime:
-                full_maxtime = full_time
-            if verts_time > verts_maxtime:
-                verts_maxtime = verts_time
-            full_steps_results.append(full_time)
-            verts_steps_results.append(verts_time)
-        full_mode_results_avg[num].append(np.mean(full_steps_results))
-        verts_mode_results_avg[num].append(np.mean(verts_steps_results))
[…]

### 2020-11-25 profiler_out/scripts/profiler_zono.py

@@ -1,130 +1,0 @@
-from matplotlib import pyplot as plt
-import numpy as np
-from nl_dynamics import F1Dynamics
-from functools import partial
-import math
-import time
-from timeit import Timer
-from run_f1zono import run_quickzono
-import pstats
-
-
-#TODO graph timing only for zono projections
-
-linear = lambda mini, maxi, frac : mini + (maxi - mini) * frac
-
-numDataTrials = 4
-
-#dt config
-dt_Min = .01
-dt_Max = .15
-dt_numSteps = 5
-dt_StepFunc = linear
-dt_Steps = [dt_StepFunc(dt_Min, dt_Max, step/(dt_numSteps)) for step in range(dt_numSteps)]
-print("DT steps are:")
-print(dt_Steps)
-
-#total time config
-ttime_Min = .5
-ttime_Max = 1
-ttime_numSteps = 2
-ttime_StepFunc = linear
-ttime_Steps = [ttime_StepFunc(ttime_Min, ttime_Max, step/(ttime_numSteps)) for step in range(ttime_numSteps)]
-print("Total Time Steps are")
-print(ttime_Steps)
-
-#tuple result pairs (ttime, dt, runtime)
-def printResult(r):
-    print("\033[0;32;40m Run complete with: runtime avg={}\n".format(r[2]))
-
-results = []
-
-maxSimSteps = 50
-#testing on dt and total
-for totalTime in ttime_Steps:
-    print("-----------------------------------")
-    print("\033[0;32;40m Running time series with: ttime={}\033[0;37;40m".format(totalTime))
-    print("-----------------------------------")
-    step_results = []
-    for dt in dt_Steps:
-        if totalTime / dt < maxSimSteps:
-            print("\033[0;32;40m Running model with : ttime={}, dt={}\033[0;37;40m".format(totalTime, dt))
-            stamp = "{}{}".format(totalTime, dt).replace('.','d')
-            runTimeTrials = []
-            print("Trials completed... \n", end='')
-            for t in range(numDataTrials):
-                print("{}".format(t+1), end=' ')
-                runTimeTrials.append(run_quickzono(dt, totalTime, [0, 0, 0], True))
-
-            #with open('profiler/raw/profile_out_{}_{}.txt'.format(dt*1000,totalTime), 'w+') as stream:
[…]

### 2020-11-25 profiler_out/scripts/hylaa_viz_node (copy).py
fix overleaf

@@ -1,97 +1,0 @@
-#!/usr/bin/python
-#node to display reachsets as filled planes in rviz
-# subscribes to hylaa output topic
-# publishes RVIZ triangle list
-# configurable in hylaa_viz.yaml
-
-import rospy
-from osuf1_common.msg import ReachSets
-import tripy
-from visualization_msgs.msg import Marker, MarkerArray
-from geometry_msgs.msg import Pose, Point, Quaternion, Vector3
-from std_msgs.msg import Header, ColorRGBA
-from osuf1_common.msg import ReachSets
-from itertools import repeat
-
-#node to publish reachability visualization messages for viewing in rviz
-
-class Hylaa_Viz_Node:
-    def __init__(self):
-        rospy.init_node("hylaa_viz")
-
-
-        reach_sub_topic = rospy.get_param("/zono_node/reach_pub_topic", "reach_pub")
-        self.reachPub = rospy.Subscriber(reach_sub_topic, ReachSets, self.makeViz) 
-        sets_outline_topic = rospy.get_param("/hylaa_viz/outline_topic", "hylaa_viz_outline")
-        sets_tris_topic = rospy.get_param("/hylaa_viz/tris_topic", "hylaa_viz_tris")
-
-        self.outlinePub = rospy.Publisher(sets_outline_topic, MarkerArray, queue_size=1)
-        self.trisPub = rospy.Publisher(sets_tris_topic, Marker, queue_size=1)
-
-        self.tri_marker_id = 44
-        self.outline_marker_id = 555 # + n
-
-        self.colors = [(230, 25, 75), (60, 180, 75), (255, 225, 25), (0, 130, 200), (245, 130, 48), (145, 30, 180), (70, 240, 240), (240, 50, 230), (210, 245, 60), (250, 190, 190), (0, 128, 128), (230, 190, 255), (170, 110, 40), (255, 250, 200), (128, 0, 0), (170, 255, 195), (128, 128, 0), (255, 215, 180), (0, 0, 128), (128, 128, 128)]
-        self.colors = [ColorRGBA(c[0], c[1], c[2], 1) for c in self.colors]
-
-    def start(self):
-        rospy.spin()
-    
-    def makeViz(self, reachSets):
-        pointSets = [[tuple(p.p) for p in rs.set] for rs in reachSets.sets]
-        triangleSets = [tripy.earclip(ps) for ps in pointSets]
-
-
-        header = Header()
-        header.stamp = rospy.Time.now()
-        header.frame_id = reachSets.header.frame_id
-
[…]

### 2020-11-25 profiler_out/scripts/kinematics_model_theano.py

@@ -1,88 +1,0 @@
-from model import Model
-import theano as th
-import theano.Tensor as T
-import numpy as np
-
-def getModel():
-    # ---------- STATE (S) -----------
-    #variables
-    x = T.dscalar('x')
-    y = T.dscalar('y')
-    p = T.dscalar('p')
-    S_k = T.dvector([x, y, p])
-
-
-    # ---------- INPUTS (U) -----------
-    #variables
-    v = T.dscalar('v')
-    d = T.dscalar('d')
-    U_k = T.dvector([v, d])
-
-    # ---------- STATE LINEARIZATION (Sbar)  -----------
-    xb = T.dscalar('xb')
-    yb = T.dscalar('yb')
-    pb = T.dscalar('pb')
-    Sbar = T.dvector([xb, yb, pb])
-
-    # ---------- INPUT LINEARIZATION (Ubar)  -----------
-    vb = T.dscalar('vb')
-    db = T.dscalar('db')
-    Ubar = T.dvector([vb, db])
-
-    # ---------- BOUNDS -----------
-    vs = T.dscalar('vs')
-    ds = T.dscalar('ds')
-    boundVars = T.dvector([vs, ds])
-
-    # ---------- CONSTANTS -----------
-    #variables
-    L = T.dscalar('L')
-    dt = T.dscalar('dt')
-    L0 = .32
-    constantVals = [L0]
-    constantSym = T.dvector([L, dt])
-
-
-    # F(Sbar, UBar)
-    F = T.dmatrix([
-        vb * cos(pb + db),
-        vb * sin(pb + db),
-        (vb/L) * sin(db)
-    ])
-
-    #find partials
-    dFdS = th.gradient.jacobian(F, Sbar)
-    dFdU = th.gradient.jacobian(F, Ubar)
-
-    #construct constant matrix
-    C = F - (dFdS * Sbar) - (dFdU * Ubar)
-
-    #define final state/inputs
-    S = S_k + [1] * C.shape[0]
-    U = U_k
-
-    #make pieces of A-matrix and combine (state dynamics)
-    M1 = dFdS  
-    M2 = np.diag(C)
-    M3 = np.zeros((Sbar.shape[0], Sbar.shape[0]))
-    M4 = np.zeros((C.shape[0], C.shape[0]))
-    
-    A_mat_func = T.stack([
-        T.stack([M1, M2], axis=2),
-        T.stack([M3, M4], axis=2)
-    ], axis=1)
[…]

### 2020-11-25 profiler_out/scripts/matplot_stored_sets.py

@@ -1,34 +1,0 @@
-from matplotlib import pyplot as plt
-
-sets = [
-    [[-0.10000000000000001, -0.10000000000000001], [0.10000000000000001, -0.10000000000000001], [0.10000000000000001, 0.10000000000000001], [-0.10000000000000001, 0.10000000000000001], [-0.10000000000000001, -0.10000000000000001]],
-    [[-0.057078379576380629, -0.11379407517118585], [-0.047437074671035757, -0.11645539036474835], [0.15256292532896426, -0.11645539036474835], [0.1534914286298294, -0.11281907676443914], [0.1534914286298294, 0.08718092323556087], [0.14385012372448452, 0.089842238429123367], [-0.056149876275515494, 0.089842238429123367], [-0.057078379576380629, 0.086205924828814159], [-0.057078379576380629, -0.11379407517118585]],
-    [[-0.0053793804683552673, -0.13283022068549016], [0.013628285161360103, -0.13906279329446952], [0.21362828516136012, -0.13906279329446952], [0.21495573596858436, -0.13469287946822447], [0.21606846581213618, -0.13045009961570725], [0.21606846581213618, 0.069549900384292762], [0.19706080018242084, 0.075782472993272121], [-0.0029391998175792022, 0.075782472993272121], [-0.0042666506248034558, 0.071412559167027073], [-0.0053793804683552673, 0.067169779314509848], [-0.0053793804683552673, -0.13283022068549016]],
-    [[0.054561493153549051, -0.15824117192077716], [0.073204714859564188, -0.16550009505145513], [0.082528545599235781, -0.16911471101579267], [0.28252854559923579, -0.16911471101579267], [0.28435186793896844, -0.16402895349055127], [0.28597888281953571, -0.15882347142324602], [0.28734116999882947, -0.15388460614986185], [0.28734116999882947, 0.046115393850138159], [0.26869794829281429, 0.053374316980816128], [0.25937411755314271, 0.05698893294515367], [0.059374117553142695, 0.05698893294515367], [0.057550795213410069, 0.051903175419912267], [0.055923780332842808, 0.046697693352607011], [0.054561493153549051, 0.041758828079222848], [0.054561493153549051, -0.15824117192077716]],
[…]

### 2020-11-25 profiler_out/scripts/model_hardcode.py

@@ -1,64 +1,0 @@
-import math
-
-#model representing the linearized dynamics 
-# and bounds of a system 
-# for use with hylaa
-
-# WHY
-# ++
-#abstracting this makes it easier to test different dynamics models 
-# through rospy settings integration
-# --
-# makes it slightly more difficult to add additional dynamics fields or matrices
-#  for use in reachability algorithm
-
-
-class Model:
-    def __init__(self):
-        self.constants = [.32, 1]
-        self.input_uncertainty = [0] * 2
-    
-    def setInputUncertainty(self, input_uncertainty):
-        print(input_uncertainty)
-        assert(len(input_uncertainty) == len(self.input_uncertainty))
-        self.input_uncertainty = input_uncertainty
-
-    def linearized_dynamics(self, state, inputs, dt):
-        #current = state+inputs+self.constants+[dt]+self.input_uncertainty
-        x, y, p = (val for val in state)
-        v, d,  = (val for val in inputs)
-        L, d0 = (val for val in self.constants)
-        # i1, i2 = input_uncertainty[1](val for val in self.input_uncertainty)
-        p_d = p + d
-        sin_p_d = math.sin(p_d)
-        cos_p_d = math.cos(p_d)
-        #sin_p_d = math.sin(p_d)
-        #cos_p_d = math.cos(p_d)
-        sin_d = math.sin(d)
-        cos_d = math.cos(d)
-
-        A = [
-            [0, 0, -v*sin_p_d, d*v*sin_p_d + p*v*sin_p_d, 0, 0],
-            [0, 0, v*cos_p_d, 0, -d*v*cos_p_d - p*v*cos_p_d, 0],
-            [0, 0, 0, 0, 0, -d*v*cos_d/L],
-            [0, 0, 0, 0, 0, 0],
-            [0, 0, 0, 0, 0, 0],
-            [0, 0, 0, 0, 0, 0]
-        ]
-
-        B = [
-            [cos_p_d, -v*sin_p_d],
-            [sin_p_d, v*cos_p_d],
-            [sin_d/L, v*cos_d/L],
-            [0, 0],
-            [0, 0],
-            [0, 0]
-        ]
-        return {
-            "A" : A,
-            "B" : B
-        }
-
-
-def getModel():
-    return Model()

### 2020-11-25 profiler_out/scripts/mpc_sim.py

@@ -1,92 +1,0 @@
-#!/usr/bin/python
-#ROS imports
-
-import rospy
-from osuf1_common.msg import MPC_metadata, MPC_trajectory, MPC_prediction
-from std_msgs.msg import Header
-from geometry_msgs.msg import PoseStamped
-from tf.transformations import euler_from_quaternion
-
-#local imports
-from nl_dynamics import F1Dynamics
-import simulator
-
-#python lib imports
-from functools import partial
-import math
-import time
-
-class MPC_Sim:
-    def __init__(self):
-
-        rospy.init_node("mpc_sim_node")
-        
-        self.nlDynamics = F1Dynamics()
-        self.stepFunc = partial(self.nlDynamics.frontStep, self.nlDynamics)
-        self.dt = rospy.get_param("/mpc_sim/dt", .1)
-        self.totalTime = rospy.get_param("/mpc_sim/total_time", 1)
-
-        self.currentState = [0, 0, 0]
-        self.inputFunc = lambda et, t : [ 4, -1 * math.cos(2*t+et)/4]
-
-#        self.simulator = simulator.ModelSimulator(self.dt, self.totalTime, self.currentState, self.stepFunc, self.inputFunc, True)
-
-        self.simulation_period = 100 #ms between publish events
-        self.prediction_pub_topic = rospy.get_param("/hylaa_node/mpc_prediction_topic", "mpc_prediction")
-        self.meta_pub_topic = rospy.get_param("/hylaa_node/mpc_metadata_topic", "mpc_metadata")
-        self.position_topic = rospy.get_param("/hylaa_node/localization_topic", "pf_pose")
-
-        self.prediction_pub = rospy.Publisher(self.prediction_pub_topic, MPC_trajectory, queue_size=1)
-        self.meta_pub = rospy.Publisher(self.meta_pub_topic, MPC_metadata, queue_size=1)
-        self.position_sub = rospy.Subscriber(self.position_topic, PoseStamped, self.parseState)
-
-        self.elapsedTime = 0
-        
-
-    def start(self):
-        rate = rospy.Rate(1000/self.simulation_period)
-        time.sleep(2)
-        while not rospy.is_shutdown():
-            results = self.simulate()
-            self.currentState = results[-1][0]
-
-            header = Header()
-            header.stamp = rospy.Time.now()
-            header.frame_id = "map"
-
-            #metadata message
-            meta = MPC_metadata()
-            meta.header = header
-            meta.dt = self.dt
-            meta.horizon = self.totalTime
[…]

### 2020-11-25 profiler_out/scripts/profiler_hylaa.py

@@ -1,124 +1,0 @@
-from matplotlib import pyplot as plt
-import numpy as np
-from nl_dynamics import F1Dynamics
-from functools import partial
-import math
-import time
-from timeit import Timer
-from run_f1hylaa import run_hylaa
-
-linear = lambda mini, maxi, frac : mini + (maxi - mini) * frac
-
-numDataTrials = 3
-
-#dt config
-dt_Min = .05
-dt_Max = .2
-dt_numSteps = 4
-dt_StepFunc = linear
-dt_Steps = [dt_StepFunc(dt_Min, dt_Max, step/(dt_numSteps-1)) for step in range(dt_numSteps)]
-print("DT steps are:")
-print(dt_Steps)
-
-#total time config
-ttime_Min = .5
-ttime_Max = 1
-ttime_numSteps = 3
-ttime_StepFunc = linear
-ttime_Steps = [ttime_StepFunc(ttime_Min, ttime_Max, step/(ttime_numSteps-1)) for step in range(ttime_numSteps)]
-print("Total Time Steps are")
-print(ttime_Steps)
-
-#tuple result pairs (ttime, dt, runtime)
-def printResult(r):
-    print("\033[0;32;40m Run complete with: runtime avg={}\n".format(r[2]))
-
-results = []
-
-maxSimSteps = 30
-#testing on dt and total
-for totalTime in ttime_Steps:
-    print("-----------------------------------")
-    print("\033[0;32;40m Running time series with: ttime={}\033[0;37;40m".format(totalTime))
-    print("-----------------------------------")
-    step_results = []
-    for dt in dt_Steps:
-        if totalTime / dt < maxSimSteps:
-            timer = Timer("""run_hylaa(dt, totalTime, [0, 0, 0], "NONE")""", globals=globals())
-            print("\033[0;32;40m Running model with : ttime={}, dt={}\033[0;37;40m".format(totalTime, dt))
-            stamp = "{}{}".format(totalTime, dt).replace('.','d')
-            runTimeTrials = []
-            print("Trials completed... \n", end='')
-            for t in range(numDataTrials):
-                print("{}".format(t+1), end=' ')
-                runTimeTrials.append(timer.timeit(1))
-
-            runTime = np.mean(runTimeTrials)
-            result = (totalTime, dt, runTime)
-            printResult(result)
[…]

### 2020-11-25 profiler_out/scripts/run_f1hylaa.py

@@ -1,60 +1,0 @@
-#barebones testing script to run hylaa without ROS
-# also used by profiler
-
-from F1Hylaa import F1Hylaa
-#local imports
-from nl_dynamics import F1Dynamics
-import simulator
-
-#python lib imports
-from functools import partial
-import math
-import time
-import xmlrpc.client
-from timeit import Timer
-
-state_uncertainty = [.1, .1, 0]
-input_uncertainty = [.1, 3.14/90] # .1m/s , 2deg
-nlDynamics = F1Dynamics()
-stepFunc = partial(nlDynamics.frontStep, nlDynamics)
-inputFunc = lambda t : [ 1+4, -1 * math.cos(2)/4]
-headless = True
-fy = F1Hylaa()
-
-def run_hylaa_profile(dt, ttime, initialState = [0, 0, 0]):
-    return run_hylaa(dt, ttime, initialState, True, False)
-
-def run_hylaa(dt, ttime, initialState, do_profile=False, output=False):
-    sim = simulator.ModelSimulator(dt, ttime, initialState, stepFunc, inputFunc, headless)
-
-    print("Simulating")
-    global predictions
-    predictions = sim.simulate()
-    print("Simulation Finished, Initializing Reachability")
-
-
-    fy.set_model_params(state_uncertainty, input_uncertainty, "kinematics_model")
-    fy.make_settings(dt, ttime, output, "VERBOSE", "hylaa.png")
-
-    print("Running HYLAA")
-    result = None
-    if do_profile:
-        timer = Timer("""fy.run_hylaa(predictions)""", globals=globals())
-        result = timer.timeit(1)
-    else:
-        result = fy.run_hylaa(predictions)
-    print("HYLAA execution finished.")
-    #print(result)
-    #print("Stateset obj")
-    #print(result[0][-3])
-    return result
-
-
-if __name__ == "__main__":
-    print("Initializing Simulation")
-    initialState = [0, 0, 0]
-    dt = .05
-    ttime = 1
-    output = "IMAGE"
-    reach = run_hylaa(dt, ttime, initialState, output)
-

### 2020-11-25 profiler_out/scripts/run_f1zono.py

@@ -1,132 +1,0 @@
-#!/home/dev/cuda-venv/bin/python3
-
-#barebones testing script to run reachability without ROS
-# also used by profiler
-
-from F1QuickZono import F1QuickZono
-
-#local imports
-from nl_dynamics import F1Dynamics
-import simulator
-
-#python lib imports
-from functools import partial
-import math
-import time
-
-import matplotlib.pyplot as plt
-import cProfile as profile
-
-#from pycallgraph import PyCallGraph
-#from pycallgraph.output import GraphvizOutput
-from timeit import Timer
-import numpy as np
-import sys
-
-gen_callgraph = False
-if gen_callgraph:
-    from pycallgraph import PyCallGraph
-    from pycallgraph import Config
-    from pycallgraph.output import GraphvizOutput
-
-state_uncertainty = [.05, .1, 0]
-input_uncertainty = [.2, 3.14/90] # .1m/s , 2deg
-nlDynamics = F1Dynamics()
-stepFunc = partial(nlDynamics.frontStep, nlDynamics)
-inputFunc = lambda t : [ 3 * t, 2 * math.sin(3.14 * t)/2]
-headless = True
-
-#modal wrappers for profiler
-def run_quickzono_CPU(dt, ttime, initialState, profile=1):
-    return run_quickzono(dt, ttime, initialState, profile, "CPU")
-
-def run_quickzono_CPU_MP(dt, ttime, initialState, profile=1):
-    return run_quickzono(dt, ttime, initialState, profile, "CPU_MP")
-
-def run_quickzono_GPU_HYBRID(dt, ttime, initialState, profile=1):
-    return run_quickzono(dt, ttime, initialState, profile, "GPU_HYBRID")
-
-def run_quickzono_GPU_DUMMY(dt, ttime, initialState, profile=1):
-    return run_quickzono(dt, ttime, initialState, profile, "GPU_DUMMY")
-
-def run_quickzono(dt, ttime, initialState, do_profile=0, runtime_mode="GPU_HYBRID"):
-    fy = F1QuickZono() 
-    fy.set_model_params(state_uncertainty, input_uncertainty, "model_hardcode", runtime_mode=runtime_mode)
-    sim = simulator.ModelSimulator(dt, ttime, initialState, stepFunc, inputFunc, headless)
-
-    #print("Simulating")
-    predictions = sim.simulate()
-    #print("Simulation Finished, Initializing Reachability")
-
[…]

### 2020-11-25 profiler_out/scripts/simulator.py

@@ -1,66 +1,0 @@
-import math
-
-#simulator for generating state approximations of nonlinear model
-# --used to create approximation used to initialize HYLAA states
-# stepFunc is as follows: (state can be any type, input must agree with inputfunc)
-
-def exampleStepFunc(state, input):
-    state[0] = state[0]
-
-    return state
-
-#inputfunc is as follows:
-
-def exampleInputFunc(time):
-    return math.cos(time) * 5 #constant modulation for this example
-
-class ModelSimulator():
-
-    def __init__(self, dt, totalTime, initialState, stepFunc=None, inputFunc=None, headless=False):
-        self.dt = dt
-        self.totalTime = totalTime
-        assert dt < totalTime, "dt >= total time - undefined configuration"
-
-        self.stepFunc = stepFunc
-        self.inputFunc = inputFunc
-        self.currentState = initialState
-
-        self.verbose = not headless
-    
-    def simulate(self, stepFunc=None, inputFunc=None):
-        if stepFunc:
-            self.stepFunc = stepFunc
-        assert self.stepFunc != None , "Step Function must be specified"
-
-        if inputFunc:
-            self.inputFunc = inputFunc 
-        assert self.inputFunc != None , "Input Function must be specified"
-
-        time = 0
-        steps = int(self.totalTime / self.dt)
-
-        if self.verbose:
-            print("Simulating {} steps with dt={}".format(steps, self.dt))
-
-        #this will store all the generated states
-        self.stateList = [(self.currentState, self.inputFunc(time))]
-
-        if self.verbose:
-            print("Initial state at time {}: \n\t{}".format(time, self.stateList[-1]))
-
-        for step in range(steps):
-            time += self.dt
-            inputs = self.inputFunc(time)
-
-            self.currentState = self.stepFunc(self.currentState, inputs, self.dt)
-            self.stateList.append((
-                self.currentState,
-                inputs
-            ))
-            
-            if self.verbose:
-                print("Step {} at time {}: \n\t{}".format(step+1, time, self.stateList[-1]))
-        
-        return self.stateList
-
-

### 2020-11-25 profiler_out/scripts/timecost.py

@@ -1,37 +1,0 @@
-import pstats
-
-from run_f1hylaa import run_hylaa
-
-
-if __name__ == "__main__":
-    print("Initializing Simulation")
-    initialState = [0, 0, 0]
-    dtList = [.02, .05, .1, .2, .5]
-    ttime = 1
-    output = "NONE"
-    numTrials = 1
-
-    top = {}
-    #run profiling for each dt
-    for dt in dtList:
-        print("With {} timesteps".format(int(ttime/dt)))
-
-        for x in range(numTrials):
-            reach = run_hylaa(dt, ttime, initialState, output)
-            print("Trial {}".format(x+1))
-            with open('profiler/raw/profile_out_{}_{}.txt'.format(dt*1000,x), 'w+') as stream:
-                p = pstats.Stats('profiler/prof/out_tmp.prof', stream=stream)
-                p = p.sort_stats("tottime").print_stats()
-        
-        with open('profiler/raw/profile_out_{}_{}.txt'.format(dt*1000,0), 'r') as tmp:
-            lines = tmp.readlines()
-            top[str(dt)] = lines[7:9]
-
-    for k,v in top.items():
-        print("{} Steps:".format(int(ttime/float(k))))
-        for func in v:
-            print("\t{}".format(func))
-            
-        
-
-

### 2020-11-25 profiler_out/scripts/zono_node.py

@@ -1,190 +1,0 @@
-#!/usr/bin/python3.6
-# library imports
-from functools import partial
-
-#local imports
-from F1QuickZono import F1QuickZono
-
-#ROS imports
-import rospy
-from std_msgs.msg import Header
-from osuf1_common.msg import MPC_trajectory, MPC_metadata, MPC_prediction, ReachSets, NPointSet, NPoint
-import time
-
-#convenience map for outputing matching mode names from online and offline profiling
-mode_format = {
-    "CPU" : "QZ_CPU",
-    "CPU_MP" : "QZ_MP",
-    "GPU_HYBRID" : "QZ_HYBRID",
-    "GPU_DUMMY" : "QZ_DUMMY",
-    "GPU" : "QZ_GPU",
-    "HYLAA" : "HYLAA"
-}
-
-class ZONO_Node:
-    def __init__(self):
-
-        rospy.init_node("zono_node")
-
-        #self.modeList = None    #store list of all modes so we can retrieve correct reachsets
-        #self.initialBox = None  #we need to store the initial stateset
-        #self.core = None        #core object for running hylaa with settings
-
-        #---------------------------------------------------------
-        #                   REACHABILITY Params
-        #---------------------------------------------------------
-        self.predictions = None #predictions from MPC
-        self.reachability_horizon = rospy.get_param("zono_node/horizon", 0)
-        self.runtime_mode = rospy.get_param("zono_node/runtime_mode", "CPU")
-        self.dt = None          #dt from MPC metdata
-        self.mpc_horizon = None #simulation horizon from MPC metadata
-
-        #TODO automatic or otherwise validated variability
-        self.state_uncertainty = [
-            rospy.get_param("zono_node/state_uncertainty/px", 0),
-            rospy.get_param("zono_node/state_uncertainty/py", 0),
-            rospy.get_param("zono_node/state_uncertainty/psi", 0),
-        ]
-        rospy.loginfo(self.state_uncertainty)
-
-        self.input_uncertainty = [
-            rospy.get_param("zono_node/input_uncertainty/velocity", 0),
-            rospy.get_param("zono_node/input_uncertainty/delta", 0)
-        ]
-
-
-        #custom horizon or utilize all computed MPC steps
-        self.hylaa_verbosity = rospy.get_param("zono_node/output_verbosity", "VERBOSE").upper() #TODO integrate with roslogger 
[…]

### 2020-11-26 paper.tex
Updates from Overleaf

@@
 A number of runtime modes which utilize single core and multiple core CPU as well as hybridized CPU/GPU were analyzed.
-In our testing we achieve accurate 10-step reachability as quickly as xxxxx seconds.
-We find that porting portions of reachability onto the GPU can improve the runtime by xxxx\% and reduces the computational complexity in relation to number of reachability steps.
+In our testing we achieve accurate 10-step reachability as quickly as 150 milliseconds.
+We also find that porting portions of reachability onto the GPU can improve the runtime for 10-step reachability by 62\% over a CPU only implementation and reduces the computational complexity in relation to number of reachability steps.
 
@@
 Reachability is the computation and interpretation of possible future agent states at a time or set of times.
-Given an agent's current state and a range of possible future inputs, a reachability algorithm outputs information about all possible states of the agent at time T in the future.
+Given an agent's current state and a range of possible future inputs, a reachability algorithm outputs information about all possible states of the agent at time $T$ in the future.
 For computational efficiency and practical use, we discuss discrete-time reachability algorithms.
-In discrete-time reachability, a range of N possible state spaces are generated for N future times.
-defined by intervals spaced by the discretization time step, dt.
+In discrete-time reachability, a range of $N$ possible state spaces are generated for $N$ future times.
+defined by intervals spaced by the discretization time step, $dt$.
 Importantly the generated state spaces are minimal overapproximations of possible states as defined by the agent’s dynamical model.
-This guarantees that any state actually reached at time T is within the overapproximation boundary and can be utilized for safety analysis.
+This guarantees that any state actually reached at time $T$ is within the overapproximation boundary and can be utilized for safety analysis.
 
@@
 In offline profiling, reachability is computed as the sole program running on the system.
-A dedicated testing script executes each of the runtime modes for 200 trials at intervals between 5 to 40 reachability steps.
-HYLAA is only tested up to 20 steps due to slow performance.
+A dedicated testing script executes each of the runtime modes for 200 trials at intervals between 4 and 24 reachability steps.
+HYLAA is only tested over 5 trials due to slow performance.
 The script outputs timing data excluding any one-off setup and configuration code.
@@
 This corresponds to either or both of an increase in horizon or decrease discretization time step.
-Horizon (sec) = \#time-step * time-step.
+$T$ = $N\cdot dt$.
 It is important to understand how the algorithm scales so intelligent decisions can be made about optimal horizon and precision in real time applications.
@@
 To validate scalability, each runtime model is tested with a range of values for the number of reachability steps which are representative of useful workloads.
-The number of steps (N) is equal to the ratio between total horizon time in seconds (T) and the discretization time-step (dt).
+The number of steps, $N$ is equal to the ratio between total horizon time in seconds, $T$ and the discretization time-step $dt$.
 This varying of step values is done for both online and offline modes.
-However, for online trials, only models capable of running around 200ms per iteration (5hz) are considered.
+However, for online trials, only models capable of running around 250ms per iteration (4hz) are considered.
 
@@
 To test runtime variability, the all recorded runtimes from all trials are analyzed.
-We compute standard deviation in runtime and 95% runtime confidence intervals around the mean assuming normally distributed variation in runtimes.
+We compute standard deviation in runtime and 95\% runtime confidence intervals around the mean assuming normally distributed variation in runtimes.
 This analysis is performed for both online and offline testing.
@@
 \begin{figure}[H]
-\includegraphics[width=\textwidth]{profiler_out/all_avg_unified.png}
-\caption{Average trial execution times for all runtime modes in online and offline configuration.} \label{fig1}
+\includegraphics[width=\textwidth]{profiler_out/offline_avg_unified.png}
+\caption{Average Offline trial execution times for all runtime modes.} \label{offline_avg}
+\end{figure}
+
+\begin{figure}[H]
+\includegraphics[width=\textwidth]{profiler_out/online_avg_unified.png}
+\caption{Average Online trial execution times for all runtime modes.} \label{online_avg}
 \end{figure}
 \begin{figure}[H]
-\includegraphics[width=\textwidth]{profiler_out/all_avg_unified.png}
-\caption{Average trial execution times for all runtime modes in online and offline configuration.} \label{fig1}
+\includegraphics[width=\textwidth]{profiler_out/avg_mp_hybrid_CI.png}
+\caption{Comparison between Multiprocessing and Hybridized online and offline runtimes.} \label{mp_hybrid_ci}
 \end{figure}
@@
 
+For offline timings, modes QZ\_CPU and QZ\_HYBRID \ref{offline_avg} show a pattern of exponential style growth.
+QZ\_DUMMY breaks this trend as we would expect since it is not doing meaningful computations for the zonotope projection algorithm which is the primary source of computational complexity.
+There is a reduction in runtime from CPU mode to QZ\_MP and QZ\_HYBRID modes indicating a that attempts at parallelization by various methods had useful impacts on the algorithms speed.
+
+Both QZ\_HYBRID and QZ\_MP are capable of running realtime reachability effectively.
+
+Online execution times show less clear patterns since it is harder to infer from the fewer data points collected.
+
 %
@@
 \bibitem{ref_hylaa}
-HYLAA Author, F., Author, S.: Title of a proceedings paper. In: Editor,
-F., Editor, S. (eds.) CONFERENCE 2016, LNCS, vol. 9999, pp. 1--13.
-Springer, Heidelberg (2016). \doi{10.10007/1234567890}
+Bak S., Sridhar Duggirala P.: HyLAA: A Tool for Computing Simulation-Equivalent Reachability for Linear Systems. In: Editor,
+Proceedings of the 20th International Conference on Hybrid Systems: Computation and Control 2017
 
+%@article{Bak2017HyLAAAT,
+%  title={HyLAA: A Tool for Computing Simulation-Equivalent Reachability for Linear Systems},
+%  author={Stanley Bak and Parasara Sridhar Duggirala},
+%  journal={Proceedings of the 20th International Conference on Hybrid Systems: Computation and Control},
+%  year={2017}
+%}
 \bibitem{ref_oder}
-ODER Author, F., Author, S., Author, T.: Book title. 2nd edn. Publisher,
-Location (1999)
+Maler O.: Computing Reachable Sets : An Introduction. 2008
+%@inproceedings{Maler2008ComputingRS,
+%  title={Computing Reachable Sets : An Introduction},
+%  author={O. Maler},
+%  year={2008}
+%}
 

### 2020-12-10 copy_media.sh
new graphs

@@ -1,1 +1,1 @@
-cp -r /home/nathan/Desktop/tx2-hosted/cuda-src/ppcm/reachability/scripts/profiler ./profiler_out
+cp -r /home/nathan/ppcm/reachability/scripts/profiler ./profiler_out

### 2020-12-10 paper.tex

@@
 \usepackage{float}
+\usepackage{todonotes}
+\usepackage{amsmath}
 % Used for displaying a sample figure. If possible, figure files should
@@
 %
-\title{Successively Linearized Onboard Reachability\thanks{Supported by organization x.}}
+\title{Embedded Reachability for Half the Price\thanks{Supported by organization x.}}
 %
@@
 \author{Nathan Jewell\inst{1}\orcidID{0000-1111-2222-3333} \and
-Houssam Abbas\inst{1}\orcidID{1111-2222-3333-4444} \and
-Stanley Baak?\inst{3}\orcidID{2222--3333-4444-5555}}
+Stanley Bak\inst{2}\orcidID{2222--3333-4444-5555} \and
+Houssam Abbas\inst{1}\orcidID{1111-2222-3333-4444}} 
 %
@@
 \email{jewelln@oregonstate.edu}}
+\institute{Stony Brook University, USA \and
+\email{jewelln@oregonstate.edu}}
 %
@@
 \begin{abstract}
-Reachability computations allow for validating safety parameters in various control systems.
-In this paper we analyze the performance characteristics of successively linearized reachability problems running in realtime.
-Importantly, we test these running alongside a full suite of autonomous control and localization tools onboard the F1/10 racing platform.
-A number of runtime modes which utilize single core and multiple core CPU as well as hybridized CPU/GPU were analyzed.
+This paper demonstrates that it is possible to obtain accurate, real-time reachability computations for an autonomous vehicle using only simple kinematics, parallelization on a GPU without any algorithmic changes, and while running a full autonomous racing stack.
+This stands in contrast to existing work which required the development of custom parallelizable reachability algorithms, the use of accurate nonlinear models of the dynamics, and was limited to a shorter look-ahead horizon.
+Reachability analysis enables the safety assurance of control systems despite uncertain initial conditions and control inputs, and can be an important component to run on-board an autonomous system.
+%The runtime of reachability analysis depend on the the system dynamics, the reachability algorithm, the hardware it is running on, and what other processes are sharing the hardware.
+%
+In this work we set out to see whether it is possible to obtain accurate and timely reachability computations using a common CPU+GPU hardware on-board an autonomous vehicle, with minimal upfront effort.
+We leverage HYLAA, a state-of-the-art reachability tool.
+Our solution uses simple linearized kinematics, yet it is accurate; runs in Python, yet is real-time; shares the hardware with a full autonomous racing stack including a state-of-the-art optimization-based predictive controller; and is partitioned between CPU and GPU without any algorithmic modifications, rather, only code-level parallelization is used.
 In our testing we achieve accurate 10-step reachability as quickly as 150 milliseconds.
-We also find that porting portions of reachability onto the GPU can improve the runtime for 10-step reachability by 62\% over a CPU only implementation and reduces the computational complexity in relation to number of reachability steps.
+We also find that porting portions of reachability onto the GPU can improve the runtime for 10-step reachability by 62\% over a CPU only implementation.% and reduces the computational complexity in relation to number of reachability steps.
+We demonstrate our results on the F1/10 1/10th-scale autonomous race car.
+This work lowers the barrier to running reachability significantly, as it removes the need to do time-consuming system identification, the need to employ nonlinear reachability tools, and the need to do an algorithm-specific modifications to enable GPU parallelization.
 
-\keywords{Reachability  \and Safety Analysis \and CUDA }
+\keywords{Reachability  \and Safety Analysis \and CUDA \and GPU}
 \end{abstract}
@@
 
-\section{Setup}
+\section{Background}
+\subsection{F1/10 Platform}
+The F1/10 autonomous racing platform is a standardized hardware platform designed to facilitate algorithmic improvements for high-reliability autonomous systems.
+The vehicle consists of a highly modified one tenth scale remote control chassis and is equipped with an improved electronic speed controller and lidar.
+The compute platform is an NVIDIA Jetson TX2 computer designed for use in embedded systems.
+The Jetson TX2 is equipped with a dual CPU setup providing 6 physical cores onboard the vehicle as well as a modern NVIDIA GPU and 8GB RAM.
+The installed autonomous navigation and mapping software is a combination of low-level nodes to interface with hardware, publicly available SLAM algorithms, and the model predictive control and reachability sofware developed in our lab.
+
+\subsection{The HYLAA Tool}
+The original HYLAA tool allows for solving linear reachability problems represented by hybrid automata with affine dynamics.
+HYLAA output is defined as a collection of reach sets.
+A reach set is the approximation of all possible \emph{reachable} states at future time $t$.
+HYLAA adopts a simulation-equivalent approach where the superposition principle for linear systems is applied to reduce the number of necessary simulations for any mode to $N+1$ for each simulated step in a N-dimensional system.
+Safety conditions represented by their linear inequalities are evaluated inline with the simulation and a variety of condition
+Basic definition of reach set, how HYLAA works (one paragraph)
+
+\subsection{QuickZono: a HYLAA variant}
+Quickzono simplifies the HYLAA algorithm, opening the possibility of realtime performance.
+Many features of HYLAA were secondary to generating the core set of reachable states and could be removed to improve performance.
+Instead of using the formalism of hybrid automata, QuickZono uses zonotopes to represent the agent state and perform the reachability simulation.
+The agent state at time $t$, $S_t$ is used to compute the next reachable set $S_{t+dt}$ at time $t + dt$ where $dt$ is the discretization step-size.
+The computation is in the form $S_{t+dt} = S_t \cdot A + I_t \cdot B$ where $I_t$ is the planned inputs at time $t$ and matrices $A, B$ are the dynamics for the system linearized around the predicted agent state given by the MPC.
+Quickzono also leaves the checking of safety conditions for post-processing step, but importantly still produces 2-dimensional projections necessary for validating these conditions in linear time.
+
+\subsection{Successively Linearzied Kinematics}
+We identified a simple 3 variable kinematic model for the car based on its physical properties.
+\begin{align}
+\dot{x} = v \cos{\psi + d} \\
+\dot{y} = v \sin{\psi + d} \\
+\dot{\psi} = v \frac{1}{L} \sin(d)
+\end{align}
+
+According to the underlying algebra of the reachability computation in HYLAA and Quickzono, $S_{t+dt} = S_t \cdot A + I_t \cdot B$, linear dynamics were computed for matrices $A_t$ and $B_t$ for state $S_t$
+
+Take a nonlinear equation $g(c)$ By definition, the linearization for g, $L_g(c)$ around a point $\bar{c}$ is given by
+
+$$L_g(c) = g(\bar{c}) + g'(\bar{c})(c-\bar{c})$$
+
+Applied to the algebra for reachability this equates
+\susection{Parallelizing Reachability}
+Initial profiling of Quickzono using pycallgraph and cProfile revealed the large portion of computation time was spent projecting from n-dimensional zonotopes onto the useful 2-dimensional polygons which can be used to analyze safety parameters in the lower dimensional agent environment.
+So, this projection step was chosen as the most impactful target for parallelization.
+The projection was particularly well suited for this because the algorithm depends only on the target zonotope and thus is trivial to parallelize across all outputed zonotopes on the CPU.
+
+GPU parallelization using CUDA was then written using a direct translation for the most time intensive function called recursively in the projection algorithm.
+A rudimentary strategy for parallelization was applied which directly translated the iterative CPU code into a single CUDA Kernel.
+Effort was taken to minimize the number of memory copies to and from the GPU and GPU compute resources were dynamically allocated depending on the number of vertices being considered in that particular projection step as well as the dimensionality of the reachability problem.
+
+\section{Experimental Setup}
 
@@
 \vspace*{-5pt}
-\subsubsection{Quickzono GPU Dummy} [QZ\_DUMMY] \newline Quickzono with data copied to and from the GPU but running\newline a dummy kernel on the GPU which does no computation of the projection. 
-\vspace*{-5pt}
 \subsubsection{Quickzono GPU Hybrid} [QZ\_HYBRID] \newline Hybrid GPU/CPU implementation, with the most taxing\newline part of the projection algorithm moved onto the GPU device. 
@@
 
-\subsection{Offline Profiling}
-In offline profiling, reachability is computed as the sole program running on the system.
+\subsection{Profiling Reachability Within the Stack}
+
+In \textit{offline} profiling, reachability is computed as the sole program running on the system.
 A dedicated testing script executes each of the runtime modes for 200 trials at intervals between 4 and 24 reachability steps.
@@
 The script outputs timing data excluding any one-off setup and configuration code.
-\subsection{Online Profiling}
-In online profiling, reachability is computed as part of a ROS network running physical control nodes (controller input, motor and servo control, etc..), a GPU based particle filter node for localization, a model predictive control node, and various other supporting nodes.
+
+In \textit{online} profiling, reachability is computed as part of a ROS network running physical control nodes (controller input, motor and servo control, etc.), a GPU-based particle filter node for localization, a model predictive control node, and various other supporting nodes.
 Before beginning the profiling, the vehicle is placed into the test track, localized and configured to autonomously drive the track until profiling is complete. 
-The reachability node is implemented as a wrapper for separate reachability classes (those called by the offline profiler) and records call timings for the same function, executing as quickly as possible.
-The online profiler is configured to automatically switch between runtimes modes and number of reachability steps.
-This occurs for the same parameters as in offline profiling except only those configurations executing at least 4hz (<=250ms per trial) are considered.
-HYLAA is not tested in this profiling due to slow performance.
+The reachability node is implemented as a wrapper for the various reachability modes described above and records call timings for the same function, executing as quickly as possible. 
+The online profiler is configured to automatically switch between runtimes modes and vary the number of reachability steps.
+This occurs for the same parameters as in offline profiling, except that only those configurations executing at least 4hz (<=250ms per trial) are considered.
+Full HYLAA is not tested in this profiling due to slow performance.
+
 \subsection{Performance Characteristics}
@@
 
-Correctness is the assuredness that the outputs are a valid solution to the problem.
-It is important to know that the algorithm is producing results consistent with the desired output and underlying mathematics.
-This is especially important for a reachability algorithm which is utilized in safety analysis protocols.
+Correctness means that the outputs are a valid solution to the problem, namely that the computed set is indeed a reachset for the dynamics.
 
-Scalability is how well the algorithm scales with increased problem size.
-In our case, problem size is dictated by the number of time steps.
-This corresponds to either or both of an increase in horizon or decrease discretization time step.
-$T$ = $N\cdot dt$.
+Scalability is how well the algorithm scales with increasing problem size.
+In our case, problem size is measured by the number $N$ of time steps.
+The number of steps is increased either by an increase in horizon $T$ or a decrease in discretization step-size $dt$, or both: $T$ = $N\cdot dt$.
 It is important to understand how the algorithm scales so intelligent decisions can be made about optimal horizon and precision in real time applications.
@@
 Runtime is the time to solve the given problem. 
-Minimizing runtime is a critical component of this research.
-Running a real time safety algorithm is only effective when there is a low latency between consecutive executions.
-If this criteria is not met, safety analysis could be out of date when the agent is developing a response, resulting in ineffective performance.
-In contrast, low latency [runtime] will improve the safety margin of the agent by providing reachability information to the controller which is very up to date with the environment.
+Running a safety algorithm is only effective when there is a low latency between consecutive executions.
+If this criterion is not met, safety analysis could be out of date when the agent is developing a response, resulting in ineffective performance or a collision.
+In contrast, low latency [runtime] will improve the safety margin of the agent by providing reachability information to the controller early enough to develop a response to it.
 
-Runtime variability is the standard deviation in the runtime.
-While latency is of primary importance, the consistency of the algorithm runtime is paramount for critical systems.
+Runtime variability is the standard deviation in the runtime. While latency is of primary importance, the consistency of the tool's runtime is paramount for autonomous systems. 
 Latency spikes at the wrong time could create dangerous problems for the agent when reacting to unsafe conditions.
@@
 
-\begin{figure}[H]
+\begin{figure}[t]
 \includegraphics[width=\textwidth]{profiler_out/offline_avg_unified.png}
@@
 
-\begin{figure}[H]
+\begin{figure}[t]
 \includegraphics[width=\textwidth]{profiler_out/online_avg_unified.png}
@@
 \end{figure}
-\begin{figure}[H]
+\begin{figure}[t]
 \includegraphics[width=\textwidth]{profiler_out/avg_mp_hybrid_CI.png}
@@
 \end{figure}
-\begin{figure}[H]
+\begin{figure}[t]
     \subcaptionbox{Detail of the Quickzono GPU Hybrid runtimes with 95\% confidence intervals.\label{CPU_CI}}{\includegraphics[width=.5\linewidth]{profiler_out/avg_QZ-CPU_CI.png} }
@@
 
-\section{Discussion}
+\subsection{Discussion}
 
@@
 %}
-
+@inproceedings{DBLP:conf/hvc/RayGDBBG15,
+  author    = {Rajarshi Ray and
+               Amit Gurung and
+               Binayak Das and
+               Ezio Bartocci and
+               Sergiy Bogomolov and
+               Radu Grosu},
+  editor    = {Nir Piterman},
+  title     = {XSpeed: Accelerating Reachability Analysis on Multi-core Processors},
+  booktitle = {Hardware and Software: Verification and Testing - 11th International
+               Haifa Verification Conference, {HVC} 2015, Haifa, Israel, November
+               17-19, 2015, Proceedings},
+  series    = {Lecture Notes in Computer Science},
+  volume    = {9434},
+  pages     = {3--18},
+  publisher = {Springer},
+  year      = {2015},
+  url       = {https://doi.org/10.1007/978-3-319-26287-1\_1},
+  doi       = {10.1007/978-3-319-26287-1\_1},
+  timestamp = {Sat, 19 Oct 2019 20:27:11 +0200},
+  biburl    = {https://dblp.org/rec/conf/hvc/RayGDBBG15.bib},
+  bibsource = {dblp computer science bibliography, https://dblp.org}
+}
 \end{thebibliography}

### 2020-12-10 copy_media.sh
new graphs w/o dummy

@@ -1,1 +1,1 @@
-cp -r /home/nathan/ppcm/reachability/scripts/profiler ./profiler_out
+cp -r /home/nathan/ppcm/reachability/scripts/profiler/ ./profiler_out

### 2020-12-10 copy_media.sh
fix media folder structure

@@ -1,1 +1,1 @@
-cp -r /home/nathan/ppcm/reachability/scripts/profiler/ ./profiler_out
+cp -r /home/nathan/ppcm/reachability/scripts/profiler ./profiler_out -T

### 2020-12-13 paper.tex
Updates from Overleaf

@@
 Planned inputs can then be modified to avoid the danger, preventing potentially catastrophic system failure.
+We compute the set of reachable states, projected onto a plane representing the agent's $x$ and $y$ coordinates in a 2d map.
 
 We explore a number of different runtime modes for profiling successively linearized reachability computation.
-These modes are chosen to stress different components of the host system, improve runtime, and demonstrate the effectiveness of real time safety analysis alongside real-world loads.
+These modes are chosen to stress different components of the host system, improve runtime, and demonstrate the impact of a functional autonomous navigation stack on performance.
 
@@
 \subsection{F1/10 Platform}
-The F1/10 autonomous racing platform is a standardized hardware platform designed to facilitate algorithmic improvements for high-reliability autonomous systems.
-The vehicle consists of a highly modified one tenth scale remote control chassis and is equipped with an improved electronic speed controller and lidar.
+Our experiments used the F1/10 autonomous racing platform which is a standardized hardware platform designed to facilitate algorithmic improvements for high-reliability autonomous systems.
+The vehicle consists of a highly modified one tenth scale remote control car chassis and is equipped with an improved electronic speed controller and LIDAR.
 The compute platform is an NVIDIA Jetson TX2 computer designed for use in embedded systems.
-The Jetson TX2 is equipped with a dual CPU setup providing 6 physical cores onboard the vehicle as well as a modern NVIDIA GPU and 8GB RAM.
-The installed autonomous navigation and mapping software is a combination of low-level nodes to interface with hardware, publicly available SLAM algorithms, and the model predictive control and reachability sofware developed in our lab.
+The Jetson TX2 is equipped with a dual CPU setup providing 6 (4+2) physical cores onboard the vehicle as well as a modern NVIDIA GPU and 8GB RAM.
+The installed autonomous navigation and mapping software is a combination of low-level nodes to interface with hardware, publicly available SLAM algorithms, and the model predictive control and reachability software developed in our lab.
 
@@
 HYLAA adopts a simulation-equivalent approach where the superposition principle for linear systems is applied to reduce the number of necessary simulations for any mode to $N+1$ for each simulated step in a N-dimensional system.
-Safety conditions represented by their linear inequalities are evaluated inline with the simulation and a variety of condition
-Basic definition of reach set, how HYLAA works (one paragraph)
+Safety conditions represented by their linear inequalities are evaluated inline with the simulation and a variety of conditions configuration options are provided to accommodate a variety of hybrid systems with changing dynamics.
 
 \subsection{QuickZono: a HYLAA variant}
-Quickzono simplifies the HYLAA algorithm, opening the possibility of realtime performance.
-Many features of HYLAA were secondary to generating the core set of reachable states and could be removed to improve performance.
+Quickzono simplifies the HYLAA algorithm, easing the implementation of realtime performance.
+Many features of HYLAA were secondary to generating the core set of reachable states in out system and are removed in QuickZono to improve performance.
 Instead of using the formalism of hybrid automata, QuickZono uses zonotopes to represent the agent state and perform the reachability simulation.
 The agent state at time $t$, $S_t$ is used to compute the next reachable set $S_{t+dt}$ at time $t + dt$ where $dt$ is the discretization step-size.
-The computation is in the form $S_{t+dt} = S_t \cdot A + I_t \cdot B$ where $I_t$ is the planned inputs at time $t$ and matrices $A, B$ are the dynamics for the system linearized around the predicted agent state given by the MPC.
-Quickzono also leaves the checking of safety conditions for post-processing step, but importantly still produces 2-dimensional projections necessary for validating these conditions in linear time.
+The computation is in the form $S_{t+dt} = S_t \cdot A + I_t \cdot B$ where $I_t$ is the planned inputs at time $t$ and matrices $A, B$ are the dynamics for the system.
+In our experiments these dynamics are linearized around the predicted agent state at that time as given by the MPC.
+QuickZono also leaves the checking of safety conditions for post-processing step, but importantly still produces 2-dimensional projections necessary for validating these conditions in linear time.
 
-\subsection{Successively Linearzied Kinematics}
+\subsection{Successively Linearized Kinematics}
 We identified a simple 3 variable kinematic model for the car based on its physical properties.
-\begin{align}
+\begin{equation}
 \dot{x} = v \cos{\psi + d} \\
@@
 \dot{\psi} = v \frac{1}{L} \sin(d)
-\end{align}
+\end{equation}
 
-According to the underlying algebra of the reachability computation in HYLAA and Quickzono, $S_{t+dt} = S_t \cdot A + I_t \cdot B$, linear dynamics were computed for matrices $A_t$ and $B_t$ for state $S_t$
+Define the state vector, $S$, formed by $x, y, \psi$
+$$S = [x, y, \psi]$$
 
-Take a nonlinear equation $g(c)$ By definition, the linearization for g, $L_g(c)$ around a point $\bar{c}$ is given by
+And the input vector, $U$, formed by $v, d$
+$$ U = [v, d]$$
+According to the underlying algebra of the reachability computation in HYLAA and Quickzono, 
+$$S_{t} = S_t \cdot A_t + U_t \cdot B$$
 
-$$L_g(c) = g(\bar{c}) + g'(\bar{c})(c-\bar{c})$$
+We find that the linear dynamics for $A$ and $B$ matrices at time $t$ are
 
-Applied to the algebra for reachability this equates
-\susection{Parallelizing Reachability}
-Initial profiling of Quickzono using pycallgraph and cProfile revealed the large portion of computation time was spent projecting from n-dimensional zonotopes onto the useful 2-dimensional polygons which can be used to analyze safety parameters in the lower dimensional agent environment.
+$$A_t = J(\dot{S}, S)\; \text{evaluated at} \;\bar{S}_t \bigcup \bar{U}_t$$
+$$B_t =  J(\dot{S}, U)\; \text{evaluated at} \;\bar{S}_t \bigcup \bar{U}_t$$
+
+Where $J(M, V)$ is the Jacobian matrix for matrix $M$ with respect to variables $V$.
+And $\bar{S}_t$ and $\bar{U}_t$ are the predicted inputs given by the MPC at time $t$.
+A tuning parameter $\alpha$ is introduced to scale the steering angle prior to evaluation of the Jacobian Matrices 
+$$\bar{S}_t = [\bar{x}, \bar{y}, \alpha\cdot\bar{\psi}]$$
+
+This parameter was added to address the problem of over or under steering in the linearized kinematics and was tuned visually to $\alpha=.5$
+
+\section{Parallelizing Reachability}
+Initial profiling of QuickZono using pycallgraph and cProfile revealed the large portion of computation time was spent projecting from n-dimensional zonotopes onto the useful 2-dimensional polygons which can be used to analyze safety parameters in the lower dimensional agent environment.
 So, this projection step was chosen as the most impactful target for parallelization.
@@
 
-GPU parallelization using CUDA was then written using a direct translation for the most time intensive function called recursively in the projection algorithm.
+GPU parallelization using CUDA was then written without modifying the underlying algorithm for the most time intensive function called recursively in the projection algorithm.
 A rudimentary strategy for parallelization was applied which directly translated the iterative CPU code into a single CUDA Kernel.
-Effort was taken to minimize the number of memory copies to and from the GPU and GPU compute resources were dynamically allocated depending on the number of vertices being considered in that particular projection step as well as the dimensionality of the reachability problem.
+Effort was taken to minimize the number of memory copies to and from the GPU and GPU and compute resources were dynamically allocated depending on the number of vertices being considered in that particular projection step as well as the dimension of the reachability problem.
 
@@
 
-For offline timings, modes QZ\_CPU and QZ\_HYBRID \ref{offline_avg} show a pattern of exponential style growth.
-QZ\_DUMMY breaks this trend as we would expect since it is not doing meaningful computations for the zonotope projection algorithm which is the primary source of computational complexity.
-There is a reduction in runtime from CPU mode to QZ\_MP and QZ\_HYBRID modes indicating a that attempts at parallelization by various methods had useful impacts on the algorithms speed.
+Realtime reachability performance at 4hz or greater was achieved for both QZ\_MP and QZ\_HYBRID runtime modes.
+This represents a significant performance improvement over QZ\_CPU for both methods of parallelization.
+We achieved an improvement in runtime based on straightforward techniques for GPU Parallelization with Nvidia CUDA.
+This is important because GPU resources are more powerful than CPU resources if they can be properly utilized.
+Process based parallelization on in QZ\_MP showed improvement larger than \%60 at 10 time steps over QZ\_CPU.
+But the multiprocessing attempt strained four CPU cores which may be better utilized in other critical applications.
 
-Both QZ\_HYBRID and QZ\_MP are capable of running realtime reachability effectively.
+Online modes had generally higher runtimes (slower) than offline modes for all steps across all rutnime modes show pvalues??.
+This is sensible due to increased CPU load in online mode from SLAM + MPC algorithms.
 
-Online execution times show less clear patterns since it is harder to infer from the fewer data points collected.
+\subsection{Further Work}
+Parallelization to the GPU left much room for improvement.
+Thorough GPU implementation of the algorithm could be a potential avenue to improved runtime complexity exceeding that of trivial CPU-based efforts.
+In larger dimensional systems, these advantages may become even more apparent.
 
@@
 \bibitem{ref_hylaa}
-Bak S., Sridhar Duggirala P.: HyLAA: A Tool for Computing Simulation-Equivalent Reachability for Linear Systems. In: Editor,
+Bak S., Sridhar Duggirala P.: HyLAA: A Tool for Computing Simulation-Equivalent Reachability for Linear Systems. In:
 Proceedings of the 20th International Conference on Hybrid Systems: Computation and Control 2017
@@
 %}
-@inproceedings{DBLP:conf/hvc/RayGDBBG15,
-  author    = {Rajarshi Ray and
-               Amit Gurung and
-               Binayak Das and
-               Ezio Bartocci and
-               Sergiy Bogomolov and
-               Radu Grosu},
-  editor    = {Nir Piterman},
-  title     = {XSpeed: Accelerating Reachability Analysis on Multi-core Processors},
-  booktitle = {Hardware and Software: Verification and Testing - 11th International
-               Haifa Verification Conference, {HVC} 2015, Haifa, Israel, November
-               17-19, 2015, Proceedings},
-  series    = {Lecture Notes in Computer Science},
-  volume    = {9434},
-  pages     = {3--18},
-  publisher = {Springer},
-  year      = {2015},
-  url       = {https://doi.org/10.1007/978-3-319-26287-1\_1},
-  doi       = {10.1007/978-3-319-26287-1\_1},
-  timestamp = {Sat, 19 Oct 2019 20:27:11 +0200},
-  biburl    = {https://dblp.org/rec/conf/hvc/RayGDBBG15.bib},
-  bibsource = {dblp computer science bibliography, https://dblp.org}
-}
+\bibitem{ref_xspeed}
+Rajarshi R.
+et.
+al., : XSpeed: Accelerating Reachability Analysis on Multi-core Processors.
+In: Piterman, N., Hardware and Software: Verification and Testing - 11th International Haifa Verification Conference, LNCS, vol.
+9434, pp.
+3--18.
+Springer, Haifa, Israel (2015)
+
+%@inproceedings{DBLP:conf/hvc/RayGDBBG15,
+%  author    = {Rajarshi Ray and
+%               Amit Gurung and
+%               Binayak Das and
+%               Ezio Bartocci and
+%               Sergiy Bogomolov and
+%               Radu Grosu},
+%  editor    = {Nir Piterman},
+%  title     = {XSpeed: Accelerating Reachability Analysis on Multi-core Processors},
+%  booktitle = {Hardware and Software: Verification and Testing - 11th International
+%               Haifa Verification Conference, {HVC} 2015, Haifa, Israel, November
+%               17-19, 2015, Proceedings},
+%  series    = {Lecture Notes in Computer Science},
+%  volume    = {9434},
+%  pages     = {3--18},
+%  publisher = {Springer},
+%  year      = {2015},
+%  url       = {https://doi.org/10.1007/978-3-319-26287-1\_1},
+%  doi       = {10.1007/978-3-319-26287-1\_1},
+%  timestamp = {Sat, 19 Oct 2019 20:27:11 +0200},
+%  biburl    = {https://dblp.org/rec/conf/hvc/RayGDBBG15.bib},
+%  bibsource = {dblp computer science bibliography, https://dblp.org}
+%}
 \end{thebibliography}

### 2020-12-13 copy_media.sh
screenshots

@@ -1,1 +1,2 @@
 cp -r /home/nathan/ppcm/reachability/scripts/profiler ./profiler_out -T
+cp -r /home/nathan/ppcm/reachability/screenshots ./screenshots -T

### 2020-12-13 paper.tex
Updates from Overleaf

--- 2020-11-26 paper.tex
@@
 \begin{abstract}
-Reachability computations allow for validating safety parameters in various control systems.
-In this paper we analyze the performance characteristics of successively linearized reachability problems running in realtime.
-Importantly, we test these running alongside a full suite of autonomous control and localization tools onboard the F1/10 racing platform.
-A number of runtime modes which utilize single core and multiple core CPU as well as hybridized CPU/GPU were analyzed.
+Reachability analysis enables the safety assurance of control systems despite uncertain initial conditions and control inputs, and can be an important component to run on-board an autonomous system.
+This tool paper demonstrates that it is possible to obtain accurate, real-time reachability computations for an autonomous vehicle using only simple kinematics, parallelization on a GPU without algorithmic changes, and while running a full autonomous racing stack.
+%This stands in contrast to existing work which required the development of custom parallelizable reachability algorithms, the use of accurate nonlinear models of the dynamics, and was limited to a shorter look-ahead horizon.
+We leverage HYLAA, a state-of-the-art reachability tool.
+Our solution uses simple linearized kinematics, yet it is accurate; runs in Python, yet is real-time; shares the hardware with a full autonomous racing stack including a state-of-the-art optimization-based predictive controller; and is partitioned between CPU and GPU using only code-level parallelization.
 In our testing we achieve accurate 10-step reachability as quickly as 150 milliseconds. 
-We also find that porting portions of reachability onto the GPU can improve the runtime for 10-step reachability by 62\% over a CPU only implementation and reduces the computational complexity in relation to number of reachability steps.
+We also find that porting portions of reachability onto the GPU can improve the runtime for 10-step reachability by 62\% over a CPU only implementation.% and reduces the computational complexity in relation to number of reachability steps.
+We demonstrate our results on the F1/10 1/10th-scale autonomous race car.
+This work lowers the barrier to running reachability significantly, as it reduces the need to do time-consuming system identification, the need to employ nonlinear reachability tools, and the need to do algorithmic modifications to enable GPU parallelization.
 
-\keywords{Reachability  \and Safety Analysis \and CUDA }
+\keywords{Reachability  \and Safety Analysis \and CUDA \and GPU}
 \end{abstract}
@@
 \section{Introduction}
-Reachability is the computation and interpretation of possible future agent states at a time or set of times.
-Given an agent's current state and a range of possible future inputs, a reachability algorithm outputs information about all possible states of the agent at time $T$ in the future.
-For computational efficiency and practical use, we discuss discrete-time reachability algorithms.
-In discrete-time reachability, a range of $N$ possible state spaces are generated for $N$ future times.
-defined by intervals spaced by the discretization time step, $dt$.
-Importantly the generated state spaces are minimal overapproximations of possible states as defined by the agent’s dynamical model.
-This guarantees that any state actually reached at time $T$ is within the overapproximation boundary and can be utilized for safety analysis.
+Reachability is the computation of possible future system states, given a set of initial states and a set of possible inputs at each time step. 
+In discrete-time reachability, a range of $N$ reach sets are computed for $N$ future times $dt$, $2dt$,..., $Ndt$, with the guarantee that any state actually reached at time $idt$ is within the $i^{th}$ computed reach set; thus the latter can be utilized for safety analysis\cite{malerintro}.
+Specifically, with safety-critical systems, it is necessary to verify that no error state could be reached.
+In autonomous vehicles, error states may involve intersections with walls, other cars or people, etc..
+By checking that the reach set does not contain error states, a guarantee is obtained that the next $N$ time steps are safe.
+Planned inputs can then be modified to avoid danger, preventing potentially catastrophic system failure.
 
-Safety verification is the overarching goal for reachability computations.
-With highly reliable systems, it is necessary to verify that no error state could be reached.
-In autonomous vehicles, error states may involve intersections with walls, other cars or people, etc..
-By checking the overapproximation of states, it can be determined if the agent is in danger of reaching an error mode in the future.
-Planned inputs can then be modified to avoid the danger, preventing potentially catastrophic system failure.
+In this work we set out to see whether it is possible to obtain accurate and timely reachability computations using a common CPU+GPU hardware on-board an autonomous vehicle, with minimal upfront effort, and while running an entire autonomous driving stack.
+Minimal effort means no system identification, no tuning of parameters, no algorithmic modifications, etc. 
+While this seems to go against the desire to have guaranteed computations, it has the advantage of significantly lowering the barrier to running reachability analysis, and we show empirically that the computations are still accurate.
+GPU based implementations of reachability include, Xspeed which introduces algorithms optimized for GPU performance.
+\cite{xspeed}.
+%We explore a number of different runtime modes for profiling reachability computation.
+These modes are chosen to stress different components of the host system, improve runtime, and demonstrate the impact of a functional autonomous navigation stack on performance.
 
-We explore a number of different runtime modes for profiling successively linearized reachability computation.
-These modes are chosen to stress different components of the host system, improve runtime, and demonstrate the effectiveness of real time safety analysis alongside real-world loads.
+\section{Background}
+\subsection{F1/10 Platform}
+Our experiments used the F1/10 autonomous racing platform which is a standardized hardware platform designed to facilitate algorithmic improvements for high-reliability autonomous systems.
+The vehicle consists of a modified one tenth scale remote control car chassis and is equipped with an improved electronic speed controller and LIDAR.
+The compute platform is an NVIDIA Jetson TX2 computer designed for use in embedded systems.
+The Jetson TX2 is equipped with a dual CPU setup providing 6 (4+2) physical cores on-board the vehicle as well as an NVIDIA GPU and 8GB RAM.
+The installed autonomous navigation and mapping software is a combination of low-level nodes to interface with hardware, publicly available SLAM algorithms, and the model predictive contour control \cite{mpcc}.
+It also includes the reachability software to be described next.
 
-\section{Setup}
+\subsection{The HYLAA Tool and its QuickZono variant}
+HYLAA \cite{hylaa} is a state-of-the-art linear reachability analysis tool - that is, it can handle linear and linear hybrid dynamical systems.
+HYLAA output is a collection of reach sets.
+A reach set is a tight over-approximation of all possible \emph{reachable} states at some future time $t$ (it is known to be theoretically impossible to obtain an exact representation of a reach set except in very special cases).
+HYLAA adopts a simulation-equivalent approach where the linear superposition principle is applied to reduce the number of necessary simulations to $N+1$ for each simulated step in a N-dimensional system.
+Safety conditions are represented as unsafe polytopes in state-space that should be avoided (a polytope is a bounded intersection of half-spaces). 
+The check of whether a reach set intersects an unsafe polytope reduces to a linear feasibility problem and is performed inline with the reachability analysis. 
+%A variety of configuration options are provided to accommodate a variety of hybrid systems with changing dynamics.
+
+\textbf{QuickZono: a HYLAA variant.}
+Quickzono simplifies the HYLAA algorithm, easing the implementation of realtime performance. 
+Many features of HYLAA were secondary to the task of generating the core set of reachable states and are removed in QuickZono.
+%Instead of using the formalism of hybrid automata, QuickZono uses zonotopes to represent the agent state and perform the reachability simulation. 
+The agent state at time $t$, $S_t$ is used to compute the next reachable set $S_{t+dt}$ at time $t + dt$ where $dt$ is the discretization step-size.
+The computation is in the form $S_{t+dt} = S_t \cdot A + I_t \cdot B$ where $I_t$ is the planned inputs at time $t$ and matrices $A, B$ are the dynamics for the system.
+In our experiments these dynamics are obtained by successive linearization as explained in the next section.
+QuickZono also defers the checking of safety conditions until after all reach sets are computed, rather than inline this check as in the default HYLAA.
+While the system state can be $N$ dimensional for any $N$, the unsafe sets for an autonomous vehicle are 2-dimensional obstacles in the $(x,y)$ plane. 
+QuickZono still produces the  2-dimensional projections of reach sets onto $(x,y)$, necessary for checking the safety conditions.
+
+\subsection{Successively Linearized Kinematics}
+\begin{figure}[t]
+    \centering
+    \includegraphics[width=.65\textwidth]{screenshots/FinalTopCorner.png}
+    \caption{Zonotope projections from a 10-step reachability problem computed in realtime (multicolored polygons).
+Visualization is rendered in Rviz and shows the rasterized map in the background, overlayed by LIDAR scan data (multicolored points), MPCC trajectory (red line), and vehicle position/heading (red arrows).
+}
+    \label{fig:my_label}
+\end{figure}
+
+We use a simple 3 variable kinematic model for the car:
+\begin{equation}
+\dot{x} = v \cos{\psi + d},~\dot{y} = v \sin{\psi + d},~\dot{\psi} = v \frac{1}{L} \sin(d)
+\end{equation}
+
+Define the state vector, $S= [x, y, \psi]$, and the input vector  $U = [v, d]$.
+The state variable $\psi$ is the current yaw of the vehicle. The input variable $d$ is the steering angle in the vehicle's frame. The constant $L=.32$ is the wheel length of the vehicle in meters. 
+An on-board Model Predictive Contouring Control  (MPCC) algorithm provides a sequence of optimal inputs for the next $N$ steps, $U_1,...,U_N$, and the corresponding predicted state trajectory is $S_1,...,S_N$.
+The non-linear kinematics are linearized around each $(S_t,U_t)$, thus obtaining the matrices $A_t,B_t$, and the linearized dynamics at step $t$ are then 
+$$S_{t+1} = S_t \cdot A_t + U_t \cdot B$$
+A tuning parameter $\alpha$ is introduced to scale the steering angle prior to evaluation of the Jacobian Matrices 
+$$\bar{S}_t = [\bar{x}, \bar{y}, \alpha\cdot\bar{\psi}]$$
+This parameter was added to address the problem of over or under steering in the linearized kinematics and was tuned experimentally to $\alpha=.5$
+
+\section{Parallelizing Reachability}
+Initial profiling of QuickZono using pycallgraph and cProfile revealed the large portion of computation time was spent projecting from n-dimensional zonotopes onto the useful 2-dimensional polygons which can be used to analyze safety parameters in the lower dimensional agent environment.
+So, this projection step was chosen as the most impactful target for parallelization.
+The projection was particularly well suited for this because the algorithm depends only on the target zonotope and thus is trivial to parallelize across all outputed zonotopes on the CPU.
+
+GPU parallelization using CUDA was then written without modifying the underlying algorithm for the most time intensive function in QuickZono which is called recursively in the projection algorithm.
+A rudimentary strategy for parallelization was applied which directly translated the iterative CPU code into a single CUDA Kernel \ref{HybridComp}.
+While this section was the most time consuming piece of code, synchronous iteration was not completely avoided for the zonotope projection.
+Convex Hull computation was not moved to the GPU, resulting in additional copies between the host and the device to occur for each iteration of the synchronous loop.
+Effort was taken to minimize the number of memory copies to and from the GPU and compute resources were dynamically allocated depending on the number of vertices being considered in that particular convex hull as well as the dimension of the reachability problem.
+This implementation method of rewriting the code directly as one CUDA kernel abuses GPU thread abstractions to simplify translation.
+However, CUDA blocks (of threads) suffer from a constrained scalability compared to CUDA grids (of blocks) due to the memory layout on Nvidia GPUs.
+So, while we used shared memory to speed communication between threads within each block we also sacrificed the parallelism afforded by much larger grid sizes in this implementation.
+
+\begin{figure}[t]
+\includegraphics[width=\textwidth]{QZ_HYBRID_COMPUTATION.png}
+\caption{The QZ\_HYBRID runtime mode implements a CPU/GPU hybrid computation model.
+Synchronous nested loops are translated to asynchronous grids of CUDA blocks in 2 dimensions.
+Matrix functions are distributed across 3 dimensions of threads within each block.
+The light blue blocks on the host and device perform analogous computations but, when executed on the GPU, as in QZ\_HYBRID, the work is distributed across hundreds of worker threads.} \label{HybridComp}
+\end{figure}
+\section{Experimental Setup}
 
 \subsection{Runtime Modes}
+We compare three ways of distributing the code between the CPU cores and the GPU cores:
 
-\subsubsection{HYLAA} \newline The original hybrid reachability tool [cite].
-\vspace*{-5pt}
-\subsubsection{Quickzono Single Core} [QZ\_CPU] \newline A simplified subset of HYLAA code with succinct wrappers. 
-\vspace*{-5pt}
-\subsubsection{Quickzono Multiple Core} [QZ\_MP] \newline Quickzono code with a trivial CPU-based multiprocessing model \newline applied to the projection step. 
-\vspace*{-5pt}
-\subsubsection{Quickzono GPU Dummy} [QZ\_DUMMY] \newline Quickzono with data copied to and from the GPU but running\newline a dummy kernel on the GPU which does no computation of the projection. 
-\vspace*{-5pt}
-\subsubsection{Quickzono GPU Hybrid} [QZ\_HYBRID] \newline Hybrid GPU/CPU implementation, with the most taxing\newline part of the projection algorithm moved onto the GPU device. 
-\vspace*{-5pt}
+%\subsubsection{HYLAA} \newline The original hybrid reachability tool [cite].
+%\vspace*{-10pt}
+\textbf{Quickzono Single Core} [QZ\_CPU]: A simplified subset of HYLAA code with succinct wrappers.
 
-\subsection{Offline Profiling}
-In offline profiling, reachability is computed as the sole program running on the system.
-A dedicated testing script executes each of the runtime modes for 200 trials at intervals between 4 and 24 reachability steps.
-HYLAA is only tested over 5 trials due to slow performance.
+\textbf{Quickzono Multiple Core} [QZ\_MP]: Quickzono code with a trivial CPU-based multiprocessing model \newline applied to the projection step.
+
+\textbf{Quickzono GPU Hybrid} [QZ\_HYBRID]: Hybrid GPU/CPU implementation, with the most taxing part of the projection algorithm moved onto the GPU device.
+
+\subsection{Profiling Reachability Within the Stack}
+
+In \textit{offline} profiling, reachability is computed as the sole program running on the system.
+
+In \textit{online} profiling, reachability is computed as part of a ROS network running physical control nodes (controller input, motor and servo control, etc.), a GPU-based particle filter node for localization, a model predictive control node, and various other supporting nodes.
+Before beginning the profiling, the vehicle is placed into the test track, localized and configured to autonomously drive the track until profiling is complete. 
+%The reachability node is implemented as a wrapper for the various reachability modes described above and records call timings for the same function, executing as quickly as possible. 
+The online profiler is configured to automatically switch between number of reachability steps.
+Between runtime modes, the reachability node is  This occurs for the same parameters as in offline profiling, except that only those configurations executing at least 4hz ($\lt$250ms per trial) are considered.
+%Full HYLAA is not tested in this profiling due to slow performance.
+
+\paragraph{Performance Characteristics}
+Evaluating an embedded reachabiltiy algorithm is done using the following metrics: 
+1) first of course is correctness: namely that the computed set is indeed a reachset for the dynamics. To validate correctness, we used HYLAA output as the ground truth.
+
+2) Next is runtime: running a safety algorithm is only effective when there is a low latency between consecutive executions.
+If this criterion is not met, safety analysis could be out of date when the agent is developing a response.
+A dedicated testing script executes each of the runtime modes for 200 trials, for $N$ reachability steps where $N$ is between 4 and 24. 
+We report average and standard deviation of runtimes over the 200 trials.
+%HYLAA is only tested over 5 trials due to slow performance. 
 The script outputs timing data excluding any one-off setup and configuration code.
-\subsection{Online Profiling}
-In online profiling, reachability is computed as part of a ROS network running physical control nodes (controller input, motor and servo control, etc..), a GPU based particle filter node for localization, a model predictive control node, and various other supporting nodes.
-Before beginning the profiling, the vehicle is placed into the test track, localized and configured to autonomously drive the track until profiling is complete.
-The reachability node is implemented as a wrapper for separate reachability classes (those called by the offline profiler) and records call timings for the same function, executing as quickly as possible.
-The online profiler is configured to automatically switch between runtimes modes and number of reachability steps.
-This occurs for the same parameters as in offline profiling except only those configurations executing at least 4hz (<=250ms per trial) are considered.
-HYLAA is not tested in this profiling due to slow performance.
-\subsection{Performance Characteristics}
-There are a number of important characteristics needed to describe the performance of a real time embedded algorithm.
 
-Correctness is the assuredness that the outputs are a valid solution to the problem.
-It is important to know that the algorithm is producing results consistent with the desired output and underlying mathematics.
-This is especially important for a reachability algorithm which is utilized in safety analysis protocols.
+3) Third is scalability with the number $N$ of reachability time steps.
 
-Scalability is how well the algorithm scales with increased problem size.
-In our case, problem size is dictated by the number of time steps.
-This corresponds to either or both of an increase in horizon or decrease discretization time step.
-$T$ = $N\cdot dt$.
-It is important to understand how the algorithm scales so intelligent decisions can be made about optimal horizon and precision in real time applications.
-
-Runtime is the time to solve the given problem.
-Minimizing runtime is a critical component of this research.
-Running a real time safety algorithm is only effective when there is a low latency between consecutive executions.
-If this criteria is not met, safety analysis could be out of date when the agent is developing a response, resulting in ineffective performance.
-In contrast, low latency [runtime] will improve the safety margin of the agent by providing reachability information to the controller which is very up to date with the environment.
-
-Runtime variability is the standard deviation in the runtime.
-While latency is of primary importance, the consistency of the algorithm runtime is paramount for critical systems.
-Latency spikes at the wrong time could create dangerous problems for the agent when reacting to unsafe conditions.
-
-\section{Methods}
-\subsection{Collected Data}
-Each characteristic has an empirical measure which we can use to analyze it quantitatively.
-Our offline and online profiling are run separately to evaluate the impact of running the reachability along with localization and control algorithms.
-
-To validate correctness, we used HYLAA model output, assuming that HYLAA is mathematically consistent.
-Outputs from other runtime modes are compared to the HYLAA output to determine if there are any significant differences.
-It is not necessary to validate correctness separately for online and offline computation since the same code is executed in each case.
-
-To validate scalability, each runtime model is tested with a range of values for the number of reachability steps which are representative of useful workloads.
-The number of steps, $N$ is equal to the ratio between total horizon time in seconds, $T$ and the discretization time-step $dt$.
-This varying of step values is done for both online and offline modes.
-However, for online trials, only models capable of running around 250ms per iteration (4hz) are considered.
-
-To test runtime, each combination of runtime mode and steps is evaluated over multiple trials.
-The recorded runtimes will be the average over 200 trials.
-This data collection is done for both online and offline testing.
-
-To test runtime variability, the all recorded runtimes from all trials are analyzed.
-We compute standard deviation in runtime and 95\% runtime confidence intervals around the mean assuming normally distributed variation in runtimes.
-This analysis is performed for both online and offline testing.
-
-Some other values are also collected for the benefit of running analysis. 
-What is a trial? One execution of the reachability computation.
+4) Finally is runtime variability: The consistency of the tool's runtime is paramount for autonomous systems. 
+Runtime spikes at the wrong time could create dangerous situations for the agent. 
+Runtime variability is measured by runtime standard deviation, and we also report the  95\% confidence intervals around the mean assuming normally distributed variation in runtimes.
 
@@
 
-\begin{figure}[H]
-\includegraphics[width=\textwidth]{profiler_out/offline_avg_unified.png}
+\begin{figure}[t]
+\includegraphics[width=.5\textwidth]{profiler_out/offline_avg_unified.png}
 \caption{Average Offline trial execution times for all runtime modes.} \label{offline_avg}
@@
 
-\begin{figure}[H]
-\includegraphics[width=\textwidth]{profiler_out/online_avg_unified.png}
+\begin{figure}[t]
+\includegraphics[width=.5\textwidth]{profiler_out/online_avg_unified.png}
 \caption{Average Online trial execution times for all runtime modes.} \label{online_avg}
 \end{figure}
-\begin{figure}[H]
-\includegraphics[width=\textwidth]{profiler_out/avg_mp_hybrid_CI.png}
+\begin{figure}[t]
+\includegraphics[width=.5\textwidth]{profiler_out/avg_mp_hybrid_CI.png}
 \caption{Comparison between Multiprocessing and Hybridized online and offline runtimes.} \label{mp_hybrid_ci}
 \end{figure}
-\begin{figure}[H]
-    \subcaptionbox{Detail of the Quickzono GPU Hybrid runtimes with 95\% confidence intervals.\label{CPU_CI}}{\includegraphics[width=.5\linewidth]{profiler_out/avg_QZ-CPU_CI.png} }
-    \subcaptionbox{Detail of the Quickzono Single Core runtimes with 95\% confidence intervals.\label{MP_CI}}{\includegraphics[width=.5\linewidth]{profiler_out/avg_QZ-MP_CI.png} }
-\begin{subfigure}{\linewidth}
-    \includegraphics[width=.5\linewidth]{profiler_out/avg_QZ-HYBRID_CI.png}
-    \includegraphics[width=.5\linewidth]{profiler_out/avg_QZ-CPU_CI.png} \hfill
 
-\end{subfigure}
+\subsection{Discussion}
 
-\end{figure}
+Realtime reachability performance at 4hz or greater was achieved for both QZ\_MP and QZ\_HYBRID runtime modes.
+This represents a significant performance improvement over QZ\_CPU for both methods of parallelization \ref{offline_avg}.
+We achieved an improvement in runtime based on straightforward techniques for GPU Parallelization with Nvidia CUDA.
+This is important because GPU resources are more powerful than CPU resources if they can be properly utilized.
+Process based parallelization on in QZ\_MP showed improvement larger than \%60 at 10 time steps over QZ\_CPU.
+But the multiprocessing attempt strained four CPU cores which may be better utilized in other critical applications.
+Notably,
 
-\section{Discussion}
+Online modes had generally higher runtimes (slower) than offline modes for all steps across all rutnime modes (show pvalues??).
+This is sensible due to increased CPU load in online mode from SLAM + MPCC algorithms.
+\ref{online_avg} Despite improved scalability of QZ\_HYBRID vs QZ\_CPU \ref{offline_avg} the two runtime modes have comparable timings at the lowest number of reachability steps.
+The overhead of making CUDA device calls for initializing GPU memory in QZ\_HYBRID may explain this discrepancy.
 
-For offline timings, modes QZ\_CPU and QZ\_HYBRID \ref{offline_avg} show a pattern of exponential style growth.
-QZ\_DUMMY breaks this trend as we would expect since it is not doing meaningful computations for the zonotope projection algorithm which is the primary source of computational complexity.
-There is a reduction in runtime from CPU mode to QZ\_MP and QZ\_HYBRID modes indicating a that attempts at parallelization by various methods had useful impacts on the algorithms speed.
-
-Both QZ\_HYBRID and QZ\_MP are capable of running realtime reachability effectively.
-
-Online execution times show less clear patterns since it is harder to infer from the fewer data points collected.
+Comparison of QZ\_MP and QZ\_HYBRID shows a much larger 95\% confidence interval for CPU\_MP  in the offline mode.
+This is unexpected given anticipated variation introduced by calling CUDA functions.
+\ref{mp_hybrid_ci} While online execution of QZ\_HYBRID is slower than QZ\_MP, offline timings are very similar for the two modes between 14 and 22 steps.
+So, performance of QZ\_HYBRID is comparable to that of QZ\_MP at these configurations despite only utilizing a single CPU core.
+This indicates a potential for reduced CPU load without sacrificing reachability performance through only naive parallelization techniques.
 
@@
 %
-% \bibliographystyle{splncs04}
-% \bibliography{mybibliography}
+\bibliographystyle{splncs04}
+\bibliography{bibliography}
 %
-\begin{thebibliography}{8}
-
-\bibitem{ref_hylaa}
-Bak S., Sridhar Duggirala P.: HyLAA: A Tool for Computing Simulation-Equivalent Reachability for Linear Systems. In: Editor,
-Proceedings of the 20th International Conference on Hybrid Systems: Computation and Control 2017
-
-%@article{Bak2017HyLAAAT,
-%  title={HyLAA: A Tool for Computing Simulation-Equivalent Reachability for Linear Systems},
-%  author={Stanley Bak and Parasara Sridhar Duggirala},
-%  journal={Proceedings of the 20th International Conference on Hybrid Systems: Computation and Control},
-%  year={2017}
-%}
-\bibitem{ref_oder}
-Maler O.: Computing Reachable Sets : An Introduction. 2008
-%@inproceedings{Maler2008ComputingRS,
-%  title={Computing Reachable Sets : An Introduction},
-%  author={O. Maler},
-%  year={2008}
-%}
-
-\end{thebibliography}
+%
 \end{document}

### 2020-12-14 paper.tex
Updates from Overleaf

@@
 \usepackage{amsmath}
+\usepackage{wrapfig}
 % Used for displaying a sample figure. If possible, figure files should
@@
 %
-\title{Embedded Reachability for Half the Price\thanks{Supported by organization x.}}
+\title{Embedded Reachability for Half the Price\thanks{Supported by NSF Award 1925500.}}
 %
@@
 %
-\author{Nathan Jewell\inst{1}\orcidID{0000-1111-2222-3333} \and
-Stanley Bak\inst{2}\orcidID{2222--3333-4444-5555} \and
-Houssam Abbas\inst{1}\orcidID{1111-2222-3333-4444}} 
+\author{Nathan Jewell\inst{1} \and
+Stanley Bak\inst{2}\and
+Houssam Abbas\inst{1}} 
 %
@@
 \institute{Oregon State University, Corvallis OR 97333, USA \and
-\email{jewelln@oregonstate.edu}}
-\institute{Stony Brook University, USA \and
-\email{jewelln@oregonstate.edu}}
+Stony Brook University, Stony Brook NY, 11794, USA}
 %
@@
 This tool paper demonstrates that it is possible to obtain accurate, real-time reachability computations for an autonomous vehicle using only simple kinematics, parallelization on a GPU without algorithmic changes, and while running a full autonomous racing stack.
+%The tool we developed, QuickZono, is a variant of HYLAA, a state-of-the-art linear reachability tool.
 %This stands in contrast to existing work which required the development of custom parallelizable reachability algorithms, the use of accurate nonlinear models of the dynamics, and was limited to a shorter look-ahead horizon.
-We leverage HYLAA, a state-of-the-art reachability tool.
-Our solution uses simple linearized kinematics, yet it is accurate; runs in Python, yet is real-time; shares the hardware with a full autonomous racing stack including a state-of-the-art optimization-based predictive controller; and is partitioned between CPU and GPU using only code-level parallelization.
+Our solution uses simple linearized kinematics, yet it is accurate; runs in Python, yet is real-time; shares the hardware with a full autonomous racing stack; and is partitioned between CPU and GPU using only code-level parallelization.
+Thus this work lowers the barrier to running reachability significantly.
 In our testing we achieve accurate 10-step reachability as quickly as 150 milliseconds. 
-We also find that porting portions of reachability onto the GPU can improve the runtime for 10-step reachability by 62\% over a CPU only implementation.% and reduces the computational complexity in relation to number of reachability steps.
+We also find that porting portions of reachability onto the GPU can improve the runtime for 10-step reachability by 62\% over a CPU-only implementation.
 We demonstrate our results on the F1/10 1/10th-scale autonomous race car.
-This work lowers the barrier to running reachability significantly, as it reduces the need to do time-consuming system identification, the need to employ nonlinear reachability tools, and the need to do algorithmic modifications to enable GPU parallelization.
-
 \keywords{Reachability  \and Safety Analysis \and CUDA \and GPU}
@@
 \section{Introduction}
-Reachability is the computation of possible future system states, given a set of initial states and a set of possible inputs at each time step. 
-In discrete-time reachability, a range of $N$ reach sets are computed for $N$ future times $dt$, $2dt$,..., $Ndt$, with the guarantee that any state actually reached at time $idt$ is within the $i^{th}$ computed reach set; thus the latter can be utilized for safety analysis\cite{malerintro}.
+For dynamical systems, \textit{reachability analysis} is the computation of possible future system states, given a \textit{set} of initial states and a \textit{set} of possible inputs at each time step.
+In discrete-time reachability, a range of $N$ reach sets are computed for $N$ future times $dt$, $2dt$,..., $Ndt$, with the guarantee that any state actually reached at time $i\cdot dt$ is within the $i^{th}$ computed reach set; thus the latter can be utilized for safety analysis \cite{malerintro}.
 Specifically, with safety-critical systems, it is necessary to verify that no error state could be reached.
@@
 By checking that the reach set does not contain error states, a guarantee is obtained that the next $N$ time steps are safe.
-Planned inputs can then be modified to avoid danger, preventing potentially catastrophic system failure.
+If not, planned inputs can then be modified to avoid danger, preventing potentially catastrophic system failure.
 
-In this work we set out to see whether it is possible to obtain accurate and timely reachability computations using a common CPU+GPU hardware on-board an autonomous vehicle, with minimal upfront effort, and while running an entire autonomous driving stack.
-Minimal effort means no system identification, no tuning of parameters, no algorithmic modifications, etc. 
-While this seems to go against the desire to have guaranteed computations, it has the advantage of significantly lowering the barrier to running reachability analysis, and we show empirically that the computations are still accurate.
-GPU based implementations of reachability include, Xspeed which introduces algorithms optimized for GPU performance.
-\cite{xspeed}.
+We have two objectives in this work: first is to enable reachability analysis for ground vehicles \textit{early in the design cycle}, so reachability itself becomes a rigorous \textit{design tool} - i.e., it is used to modify the design to better separate reach sets from error states.
+This requires the ability to run reachability with minimal up-front effort, in real-time.
+Minimal effort means using a simple dynamical model, little to no system identification, and no algorithmic modifications. 
+Our second objective is to equip the F1/10 autonomous racing platform with an easy-to-use reachability tool. 
+F1/10 (see f1tenth.org) is an open-source hardware and software platform for autonomous systems research and education, in use in tens of universities in the US and around the world, and the F1/10 project hosts yearly autonomous races.
+To enable formal methods education, and to make the platform safer for research and racing, reachability is an essential component. 
+Embedded reachability on-board F1/10 must run out-of-the-box.
+Because different groups will have slightly different builds of the car, we cannot require custom dynamical models and system identification.
+
+In this work we developed QuickZono, a variant of HYLAA\cite{hylaa}, a state-of-the-art linear reachability tool.
+We show empirically, via experiments on the F1/10 race car, that the computations are still accurate, and real-time.
+
+\paragraph{Related work}.
+GPU-based implementations of dynamical systems reachability include Xspeed which introduces algorithms optimized for GPU performance \cite{xspeed}.
+Xspeed modifies reachability algorithms to enable GPU parallelization, unlike our approach.
+Because we use simple linearized kinematics, we also achieve faster runtimes compared to what's reported in~\cite{xspeed}.
+The work in \cite{althoff} does real-time reachability on a non-linear model which requires systems identification, which is a step we seek to avoid.
 %We explore a number of different runtime modes for profiling reachability computation.
@@
 \subsection{F1/10 Platform}
-Our experiments used the F1/10 autonomous racing platform which is a standardized hardware platform designed to facilitate algorithmic improvements for high-reliability autonomous systems.
-The vehicle consists of a modified one tenth scale remote control car chassis and is equipped with an improved electronic speed controller and LIDAR.
-The compute platform is an NVIDIA Jetson TX2 computer designed for use in embedded systems.
-The Jetson TX2 is equipped with a dual CPU setup providing 6 (4+2) physical cores on-board the vehicle as well as an NVIDIA GPU and 8GB RAM.
-The installed autonomous navigation and mapping software is a combination of low-level nodes to interface with hardware, publicly available SLAM algorithms, and the model predictive contour control \cite{mpcc}.
-It also includes the reachability software to be described next.
+Our experiments used the F1/10 autonomous race car, which is an open-source platform designed for research and education on high-reliability autonomous systems.
+The F1/10 vehicle consists of a modified one tenth-scale remote control car chassis and is equipped with an improved electronic speed controller and LIDAR.
+The compute platform is an embedded NVIDIA Jetson TX2 computer.
+The Jetson TX2 is equipped with a dual CPU setup providing 6 (4+2) physical cores as well as a 256-core NVIDIA GPU and 8GB RAM.
+F1/10 runs a combination of low-level nodes to interface with hardware, publicly available SLAM algorithms, and a state-of-the-art model predictive contour controller \cite{mpcc}.
+It also includes the reachability software described next.
 
 \subsection{The HYLAA Tool and its QuickZono variant}
-HYLAA \cite{hylaa} is a state-of-the-art linear reachability analysis tool - that is, it can handle linear and linear hybrid dynamical systems.
+HYLAA \cite{hylaa} is a state-of-the-art linear reachability analysis tool - that is, it can handle linear hybrid dynamical systems.
 HYLAA output is a collection of reach sets.
-A reach set is a tight over-approximation of all possible \emph{reachable} states at some future time $t$ (it is known to be theoretically impossible to obtain an exact representation of a reach set except in very special cases).
-HYLAA adopts a simulation-equivalent approach where the linear superposition principle is applied to reduce the number of necessary simulations to $N+1$ for each simulated step in a N-dimensional system.
+%A reach set is a tight over-approximation of all possible \emph{reachable} states at some future time $t$ (it is known to be theoretically impossible to obtain an exact representation of a reach set except in very special cases).
+%HYLAA adopts a simulation-equivalent approach where the linear superposition principle is applied to reduce the number of necessary simulations to $N+1$ for each simulated step in a N-dimensional system.
 Safety conditions are represented as unsafe polytopes in state-space that should be avoided (a polytope is a bounded intersection of half-spaces). 
@@
 \textbf{QuickZono: a HYLAA variant.}
-Quickzono simplifies the HYLAA algorithm, easing the implementation of realtime performance. 
-Many features of HYLAA were secondary to the task of generating the core set of reachable states and are removed in QuickZono.
+QuickZono is a variant of HYLAA which we obtained by disabling certain unneeded features, and by GPU parallelization, as described in Section~\ref{sec:Parallelizing Reachability}. 
+We did not modify the core HYLAA algorithms.
+Many features of HYLAA were secondary to the task of generating the core set of reachable states.
+Thus we disabled them.
 %Instead of using the formalism of hybrid automata, QuickZono uses zonotopes to represent the agent state and perform the reachability simulation. 
-The agent state at time $t$, $S_t$ is used to compute the next reachable set $S_{t+dt}$ at time $t + dt$ where $dt$ is the discretization step-size.
+%The agent state at time $t$, $S_t$ is used to compute the next reachable set $S_{t+dt}$ at time $t + dt$ where $dt$ is the discretization step-size.
 The computation is in the form $S_{t+dt} = S_t \cdot A + I_t \cdot B$ where $I_t$ is the planned inputs at time $t$ and matrices $A, B$ are the dynamics for the system.
-In our experiments these dynamics are obtained by successive linearization as explained in the next section.
-QuickZono also defers the checking of safety conditions until after all reach sets are computed, rather than inline this check as in the default HYLAA.
-While the system state can be $N$ dimensional for any $N$, the unsafe sets for an autonomous vehicle are 2-dimensional obstacles in the $(x,y)$ plane. 
+%In our experiments these dynamics are obtained by successive linearization as explained in the next section.
+While the system state can be $n$ dimensional for any $n$, the unsafe sets for an autonomous vehicle are 2-dimensional obstacles in the $(x,y)$ plane. 
 QuickZono still produces the  2-dimensional projections of reach sets onto $(x,y)$, necessary for checking the safety conditions.
+QuickZono also defers the checking of safety conditions until after all reach sets are computed, rather than inline this check as in HYLAA.
 
 \subsection{Successively Linearized Kinematics}
-\begin{figure}[t]
-    \centering
-    \includegraphics[width=.65\textwidth]{screenshots/FinalTopCorner.png}
-    \caption{Zonotope projections from a 10-step reachability problem computed in realtime (multicolored polygons).
-Visualization is rendered in Rviz and shows the rasterized map in the background, overlayed by LIDAR scan data (multicolored points), MPCC trajectory (red line), and vehicle position/heading (red arrows).
-}
-    \label{fig:my_label}
-\end{figure}
 
@@
 \end{equation}
-
+where the state variable $\psi$ is the current yaw of the vehicle.
+The input variable $d$ is the steering angle in the vehicle's frame.
+The constant $L=.32$ is the wheel length of the vehicle in meters.
 Define the state vector, $S= [x, y, \psi]$, and the input vector  $U = [v, d]$.
-The state variable $\psi$ is the current yaw of the vehicle. The input variable $d$ is the steering angle in the vehicle's frame. The constant $L=.32$ is the wheel length of the vehicle in meters. 
 An on-board Model Predictive Contouring Control  (MPCC) algorithm provides a sequence of optimal inputs for the next $N$ steps, $U_1,...,U_N$, and the corresponding predicted state trajectory is $S_1,...,S_N$.
-The non-linear kinematics are linearized around each $(S_t,U_t)$, thus obtaining the matrices $A_t,B_t$, and the linearized dynamics at step $t$ are then 
-$$S_{t+1} = S_t \cdot A_t + U_t \cdot B$$
-A tuning parameter $\alpha$ is introduced to scale the steering angle prior to evaluation of the Jacobian Matrices 
+The non-linear kinematics are linearized around each $(S_t,U_t)$, thus obtaining the matrices $A_t,B_t$, and the linearized dynamics at step $t$ are then $S_{t+1} = S_t \cdot A_t + U_t \cdot B$.
+A correction parameter $\alpha$ is introduced to scale the steering angle prior to evaluation of the Jacobian matrices 
 $$\bar{S}_t = [\bar{x}, \bar{y}, \alpha\cdot\bar{\psi}]$$
 This parameter was added to address the problem of over or under steering in the linearized kinematics and was tuned experimentally to $\alpha=.5$ 
+See Fig.~\ref{fig:correctness}.
+
+\begin{wrapfigure}{R}{.5\textwidth}
+    \centering
+    \includegraphics[width=.48\textwidth]{screenshots/FinalTopCorner.png}
+    \caption{Zonotope projections from a 10-step reachability problem computed in realtime (multicolored polygons).
+Visualization is rendered in Rviz and shows the rasterized map in the background, overlayed by LIDAR scan data (multicolored points), MPCC trajectory (red line), and vehicle position/heading (red arrows).
+Note the MPCC trajectory lies inside the reach sets.}
+    \label{fig:correctness}
+\end{wrapfigure}
 
 \section{Parallelizing Reachability}
+\label{sec:Parallelizing Reachability}
 Initial profiling of QuickZono using pycallgraph and cProfile revealed the large portion of computation time was spent projecting from n-dimensional zonotopes onto the useful 2-dimensional polygons which can be used to analyze safety parameters in the lower dimensional agent environment.
 So, this projection step was chosen as the most impactful target for parallelization.
-The projection was particularly well suited for this because the algorithm depends only on the target zonotope and thus is trivial to parallelize across all outputed zonotopes on the CPU.
+The projection was particularly well suited for this because it depends only on the target zonotope and thus is conceptually easy to parallelize across all $N$ output zonotopes.
 
 GPU parallelization using CUDA was then written without modifying the underlying algorithm for the most time intensive function in QuickZono which is called recursively in the projection algorithm.
-A rudimentary strategy for parallelization was applied which directly translated the iterative CPU code into a single CUDA Kernel \ref{HybridComp}.
+The iterative CPU code was directly translated into a single CUDA Kernel ~\ref{fig:HybridComp}.
 While this section was the most time consuming piece of code, synchronous iteration was not completely avoided for the zonotope projection.
@@
 This implementation method of rewriting the code directly as one CUDA kernel abuses GPU thread abstractions to simplify translation. 
-However, CUDA blocks (of threads) suffer from a constrained scalability compared to CUDA grids (of blocks) due to the memory layout on Nvidia GPUs.
+However, CUDA blocks (of threads) suffer from a constrained scalability compared to CUDA grids (of blocks) due to the memory layout on Nvidia GPUs ~\cite{cuda}. 
 So, while we used shared memory to speed communication between threads within each block we also sacrificed the parallelism afforded by much larger grid sizes in this implementation.
@@
 Matrix functions are distributed across 3 dimensions of threads within each block.
-The light blue blocks on the host and device perform analogous computations but, when executed on the GPU, as in QZ\_HYBRID, the work is distributed across hundreds of worker threads.} \label{HybridComp}
+The light blue blocks on the host and device perform analogous computations but, when executed on the GPU, as in QZ\_HYBRID, the work is distributed across hundreds of worker threads.} \label{fig:HybridComp}
 \end{figure}
@@
 In \textit{offline} profiling, reachability is computed as the sole program running on the system. 
-
 In \textit{online} profiling, reachability is computed as part of a ROS network running physical control nodes (controller input, motor and servo control, etc.), a GPU-based particle filter node for localization, a model predictive control node, and various other supporting nodes.
-Before beginning the profiling, the vehicle is placed into the test track, localized and configured to autonomously drive the track until profiling is complete. 
+The MPCC is configured to use 15 time steps of .15 sec each, generating control inputs at a rate of about 20hz.
+%Before beginning the profiling, the vehicle is placed into the test track, localized and configured to autonomously drive the track until profiling is complete. 
 %The reachability node is implemented as a wrapper for the various reachability modes described above and records call timings for the same function, executing as quickly as possible.
-The online profiler is configured to automatically switch between number of reachability steps.
-Between runtime modes, the reachability node is  This occurs for the same parameters as in offline profiling, except that only those configurations executing at least 4hz ($\lt$250ms per trial) are considered.
-%Full HYLAA is not tested in this profiling due to slow performance.
 
 \paragraph{Performance Characteristics}
-Evaluating an embedded reachabiltiy algorithm is done using the following metrics: 
+Evaluating an embedded reachability algorithm is done using the following metrics: 
 1) first of course is correctness: namely that the computed set is indeed a reachset for the dynamics. To validate correctness, we used HYLAA output as the ground truth.
-
+%
 2) Next is runtime: running a safety algorithm is only effective when there is a low latency between consecutive executions.
-If this criterion is not met, safety analysis could be out of date when the agent is developing a response.
+Otherwise, safety analysis results could be too late for the agent to develop a response.
 A dedicated testing script executes each of the runtime modes for 200 trials, for $N$ reachability steps where $N$ is between 4 and 24. 
@@
 The script outputs timing data excluding any one-off setup and configuration code.
-
+%
 3) Third is scalability with the number $N$ of reachability time steps. 
-
+%
 4) Finally is runtime variability: The consistency of the tool's runtime is paramount for autonomous systems.
@@
 \begin{figure}[t]
-\includegraphics[width=.5\textwidth]{profiler_out/offline_avg_unified.png}
-\caption{Average Offline trial execution times for all runtime modes.} \label{offline_avg}
+\centering
+\begin{minipage}{.5\textwidth}
+    \centering
+    \includegraphics[width=\linewidth]{profiler_out/offline_avg_unified.png}
+    \caption{Average Offline trial execution times for all runtime modes.} \label{fig:offline_avg}
+\end{minipage}%
+\begin{minipage}{.5\textwidth}
+    \includegraphics[width=\linewidth]{profiler_out/online_avg_unified.png}
+    \caption{Average Online trial execution times for all runtime modes.} \label{fig:online_avg}
+\end{minipage}
 \end{figure}
-
-\begin{figure}[t]
-\includegraphics[width=.5\textwidth]{profiler_out/online_avg_unified.png}
-\caption{Average Online trial execution times for all runtime modes.} \label{online_avg}
-\end{figure}
-\begin{figure}[t]
-\includegraphics[width=.5\textwidth]{profiler_out/avg_mp_hybrid_CI.png}
-\caption{Comparison between Multiprocessing and Hybridized online and offline runtimes.} \label{mp_hybrid_ci}
-\end{figure}
-
-\subsection{Discussion}
+\begin{wrapfigure}{L}{.5\textwidth}
+\includegraphics[width=.48\textwidth]{profiler_out/avg_mp_hybrid_CI.png}
+\caption{Comparison between Multiprocessing and Hybridized online and offline runtimes.} \label{fig:mp_hybrid_ci}
+\end{wrapfigure}
 
 Realtime reachability performance at 4hz or greater was achieved for both QZ\_MP and QZ\_HYBRID runtime modes.
-This represents a significant performance improvement over QZ\_CPU for both methods of parallelization \ref{offline_avg}.
+This represents a significant performance improvement over QZ\_CPU for both methods of parallelization ( Fig.
+~\ref{fig:correctness}).
 We achieved an improvement in runtime based on straightforward techniques for GPU Parallelization with Nvidia CUDA.
@@
 
-Online modes had generally higher runtimes (slower) than offline modes for all steps across all rutnime modes (show pvalues??).
-This is sensible due to increased CPU load in online mode from SLAM + MPCC algorithms.
-\ref{online_avg} Despite improved scalability of QZ\_HYBRID vs QZ\_CPU \ref{offline_avg} the two runtime modes have comparable timings at the lowest number of reachability steps.
+Online modes had generally higher runtimes (slower) than offline modes for all steps across all rutnime modes.
+This is sensible due to increased CPU load in online mode from SLAM + MPCC algorithms (Fig.
+~\ref{fig:online_avg}) Despite improved scalability of QZ\_HYBRID vs QZ\_CPU (Fig.
+~\ref{fig:offline_avg}) the two runtime modes have comparable timings at the lowest number of reachability steps.
 The overhead of making CUDA device calls for initializing GPU memory in QZ\_HYBRID may explain this discrepancy.
@@
 Comparison of QZ\_MP and QZ\_HYBRID shows a much larger 95\% confidence interval for CPU\_MP  in the offline mode.
-This is unexpected given anticipated variation introduced by calling CUDA functions.
-\ref{mp_hybrid_ci} While online execution of QZ\_HYBRID is slower than QZ\_MP, offline timings are very similar for the two modes between 14 and 22 steps.
+This is unexpected given anticipated variation introduced by calling CUDA functions (Fig.
+~\ref{fig:mp_hybrid_ci}).
+While online execution of QZ\_HYBRID is slower than QZ\_MP, offline timings are very similar for the two modes between 14 and 22 steps.
 So, performance of QZ\_HYBRID is comparable to that of QZ\_MP at these configurations despite only utilizing a single CPU core.
